\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amsthm, amsfonts, amssymb}
\usepackage{mathtools}
\usepackage{tikz-cd}
\usepackage{enumerate}
\usepackage[hidelinks, unicode]{hyperref}
\usepackage{cleveref}
\usepackage[style=alphabetic]{biblatex}

\addbibresource{bibliography.bib}

\theoremstyle{plain}% default
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem*{note}{Note}
\newtheorem{case}[theorem]{Case}
\newtheorem*{notation}{Notation}

\newcommand{\cob}{\mathcal{C}_\mathcal{O}^\bullet}
\newcommand{\co}{\mathcal{C}_\mathcal{O}}
\newcommand{\ann}{\operatorname{Ann}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\fitt}{\operatorname{Fitt}}
\renewcommand{\hom}{\operatorname{Hom}}
\newcommand{\GL}{\operatorname{GL}}

\title{Wiles' numerical criterion}
\author{Josua Kugler}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{A brief sketch of the proof of Fermat's Last Theorem}
\subsection{Fermat's Last Theorem and the modularity conjecture}
\begin{theorem}[Fermat's Last Theorem]
    There are no \(a, b, c \in \mathbb{Z}\) with \(abc \neq 0\) and \(n \in \mathbb{N}, n \geq 3\) such that
    \[
        a^n + b^n = c^n.  
    \]
\end{theorem}
This is equivalent to
\begin{theorem}
    There are no \(a, b, c \in \mathbb{Z}\) with \(abc \neq 0\) and a prime number \(p \geq 5\) such that
    \[
        a^p + b^p = c^p.  
    \]
\end{theorem}
Indeed, let \(a^n + b^n = c^n\) be a solution of the Fermat equation where \(n \geq 3\).
In the latter case, \(n\) is always divided by a prime number \(\geq 3\) or by \(4\).
We can then write \(n = \tilde{p} \cdot m\) where \(\tilde p \in \{4\} \cup \{p | p \text{ odd prime}\}\)
and obtain 
\[
    a^n + b^n = c^n \Leftrightarrow (a^m)^{\tilde p} + (b^m)^{\tilde p} = (c^m)^{\tilde p}.  
\]
The case \(\tilde p = 4\) has been ruled out by Fermat himself and the case \(\tilde p = 3\)
was shown soon after, so any solution of the Fermat equation of exponent \(n\) 
induces a solution of the Fermat equation for some prime number \(p\geq 5\).

One of the key breakthroughs in the proof of FLT was to consider the
\begin{definition}[Frey-Hellegouarch-Curve]
    From a solution of the Fermat equation we can with little technical modifications obtain a triple \((a,b,c)\) 
    such that \(a^p + b^p + c^p = 0\), \(a \cong -1 \mod 4, 2|b\). Then define the elliptic curve
    \[
        E_{a,b,c}\colon y^2 = x(x-a^p)(x+b^p).
    \]
\end{definition}
The existence of such a curve contradicts several well-known 
conjectures (such as Serre's conjecture, cf. next section) 
and Frey therefore conjectured that such a curve couldn't exist.
He suggested to prove this by associating a modular form to this curve and showing that this modular form couldn't exist.
The key point in this strategy was the following
\begin{theorem}[Modularity]\label{th:modularity}
    Every semistable elliptic curve over \(\mathbb Q\) is modular, i.e. there is a modular form \(f\) "associated" to \(E\)
    in a sence that will be made precise in the next sections.
\end{theorem}
When Frey had the idea of using this to prove FLT, \cref{th:modularity} still was a conjecture.
It was finally proved by Andrew Wiles and Richard Taylor in 1995.
(In the years until 1999 the semistability condition could be removed, so that
the theorem holds for all elliptic curves.)

\subsection{Galois representations and modularity}

\paragraph{Definitions}
Let \(A\) be a complete noetherian local ring with finite residue field \(k\).
A continuous group homomorphism
\[
    \rho\colon G_\mathbb{Q} \to \GL_2(A)
\]
is called a Galois representation, where \(G_\mathbb{Q}\) is endowed with the Krull topology.
By reducing to the residue field, we obtain the residual representation
\[
    \overline{\rho}\colon G_\mathbb{Q} \to \GL_2(k),
\]
where the topology on \(k\) is the discrete topology.
A residual representation can have multiple lifts. Two such lifts \(\rho, \rho'\) are called equivalent
if \(\rho' = M\rho M^{-1}\) for \(M \in \GL_2(A)\) s.t. \(M \equiv \mathrm{id}_{2} \mod \mathfrak{m}_A\).
An equivalence class of lifts of \(\rho_0\) is called deformation of \(\rho\).

\begin{definition}
    A Galois representation \(\rho\) is \textbf{odd} if \(\rho(c) = -1\) where \(c\) denotes the generator
    of \(G_{\mathbb{Q}_\infty}\). Note that \(G_{\mathbb{Q}_\infty}\) is canonically isomorphic to
    the decomposition subgroup associated to \(\infty\) in \(G_\mathbb{Q}\).
\end{definition}
\begin{definition}
    A Galois representation \(\rho\) is \textbf{unramified} at \(\ell\) if the inertia group
    \(I_\ell\) is contained in the kernel of \(\rho\).
    Being \textbf{flat} is a condition of similar nature, though considerably more technical.
\end{definition}

\paragraph{Galois representations for elliptic curves}
As it is very difficult to come from an elliptic curve to a modular form directly, 
Wiles chose an indirect way via Galois representations.
For each elliptic curve \(E\) over \(\mathbb{Q}\), we can associate a Galois representation as follows.
%explain how we get an operation of G_Q on the Tate-module
Take the \(p\)-torsion subgroup \(E[p]\) of \(E\) (i.e. the kernel of \(p\)-multiplication on \(E\)).
It is well known that we can choose a generating system \(P, Q\) for \(E[p]\) and 
obtain an isomorphism \(E[p] \cong (\mathbb{Z}/p \mathbb{Z})^2\).
As \(\mathbb{Q}(E[p])\) is a Galois number field, it is not hard to see that we have
a continuous Galois operation on \(E[p]\), i.e. a morphism
\[
    \operatorname{Gal}(\mathbb{Q}(E[p])/\mathbb{Q}) \to \GL_2(\mathbb{Z}/p\mathbb{Z}).  
\]
Completely analogous, we can construct compatible morphisms for \(E[p^n]\) 
and in the limit we obtain a map
\[
    \rho_{E, p} \colon G_\mathbb{Q} \to \GL_2(\mathbb{Z}_p).
\]
One can show that \(\rho_{E,p}\) is continuous with respect to the \(p\)-adic topology,
i.e. \(\rho_{E,p}\) is a Galois representation.

\begin{proposition}\cite[chapter 1, theorem 2.11]{Cornell1997}\label{prop:rhoEpproperties} 
    Let \(N_E\) be the conductor of \(E\) and \(\rho_{E,p}\) the representation described above.
    Then
    \begin{itemize}
        \item \(\det \rho_{E,p} = \chi_p\),
        \item \(\rho_{E,p}\) is unramified at primes not dividing \(pN_E\), and
        \item \(\rho_{E, p}\) is odd.
    \end{itemize}
    If \(E\) is semistable and \(\Delta_E\) its minimal discriminant, we can further conclude that for
    \[
        \overline{\rho}_{E,p}\colon G_Q \to \GL_2(\mathbb{Z}/p\mathbb{Z})  
    \]
    the following equivalences hold.
    \begin{itemize}
        \item \(\overline{\rho}_{E,p}\) is flat at \(p\) \(\Leftrightarrow p| \operatorname{ord}_p(\Delta_E)\).
        \item For any prime \(\ell \neq p\): 
        \(\overline{\rho}_{E,p}\) is unramified at \(\ell\) \(\Leftrightarrow p| \operatorname{ord}_\ell(\Delta_E)\).
    \end{itemize}
\end{proposition}

\paragraph{Galois representations for modular forms}
Now that we have seen how to associate a Galois representation to an elliptic curve, we want to
do the same thing for a modular form. However, this is far more difficult and therefore beyond 
the scope of this thesis.
The result that we need is that to a new cuspform \(f\) of weight \(2\) we can associate a p-adic 
Galois representation \(\rho_f\) \cite[see][section 9.5]{Diamond2007}.
Now we can state Serre's conjecture that was mentioned in the introduction.
Let
\[
    \rho\colon G_\mathbb{Q} \to \GL_2(\mathbb{F}_p)
\]
be a continuous, odd, irreducible Galois representation. 
Then there exists a cuspidal eigenform \(f\) such that 
\[
    \rho \cong \rho_f.
\]
Serre even gives detailed formulas that assert a certain weight and level for \(f\).
In the case of \(\rho_{E_{a,b,c},p}\) it predicts level two and weight two, a contradiction 
because the space of weight 2 modular forms of level 2 is zero.
That might be one of the reasons why Frey  conjectured that they Frey curve \(E_{a,b,c}\) couldn't exist.

\paragraph{Modularity}
A Galois representation \(\rho\) is modular if there is a newform \(f\) of weight \(2\) such that
\[
    \rho \cong \rho_f. 
\]
For elliptic curves \(E/\mathbb{Q}\) we have the following definition/theorem.
\begin{theorem}\cite[chapter 1, theorem 5.1]{Cornell1997}\label{th:eqcondmodularity}
    An elliptic curve \(E/\mathbb{Q}\) with conductor \(N_E\) is modular if it satisfies the following equivalent conditions.
    \begin{enumerate}
        \item For some prime \(p\), \(\rho_{E,p}\) is modular.
        \item For all primes \(p\), \(\rho_{E,p}\) is modular.
        \item There is a newform \(f\) of weight \(2\) and level \(N_E\) s.t. \(L(f, s) = L(E, s)\).
        \item There is a non-constant morphism \(\pi\colon X_0(N_E) \to E\) of algebraic curves over \(\mathbb{Q}\).
        \item There is an isogeny \(E \to A_f\), where \(A_f\) is the modular abelian variety associated to a
        weight \(2\) newform \(f\) of conductor \(N_E\).
    \end{enumerate}
    The last three equivalences are of no further relevance to the thesis but might be of interest to the reader.
\end{theorem}

\subsection{Ribet's theorem and the contradiction}
For a moment, let's believe that every semistable elliptic curve is modular.
In order to prove FLT, we need one more deep ingredient, namely
\begin{theorem}[Ribet's theorem]
    Let \(f\) be a newform of weight \(2\) and level \(N\ell\) for a prime \(\ell\) s.t. \(\ell\not | N\).
    Suppose that the associated Galois representation \(\overline{\rho}_f\) is absolutely irreducible
    and satisfies one of the following conditions.
    \begin{itemize}
        \item \(\overline{\rho}_f\) is unramified at \(\ell\)
        \item \(\ell = p\) and \(\overline{\rho}_f\) is flat at \(p\).
    \end{itemize}
    Then there is a newform of weight \(2\) and level \(N\) such that
    \[
        \overline{\rho}_f \cong \overline{\rho}_g.
    \]    
\end{theorem}
By modularity (cf. \cref{th:eqcondmodularity}) we find a newform \(f\) of weight \(2\) such that
\[
    \overline{\rho}_{E_{a,b,c}, p} \cong \overline{\rho}_f
\]
We need the semistability of \(E_{a,b,c}\) and the properties shown in \cref{prop:rhoEpproperties}.
Because of the specific properties of the Frey curve we have the following finer results for \(\rho_{E_{a,b,c}, p}\) 
\cite[see][chapter 1, theorem 3.1]{Cornell1997}.
\begin{itemize}
    \item \(\rho_{E_{a,b,c}, p}\) is absolutely irreducible
    \item \(\rho_{E_{a,b,c}, p}\) is unramified outside \(2p\) and flat at \(p\) %and semistable at \(2\).
\end{itemize} %TODO: We need these results for the reduction!
As \(E\) is semistable, the conductor is squarefree,
\[ 
    N_E = 2 \cdot p \cdot \prod_{\ell\in S \text{ prime}} \ell
\]
for a finite set \(S\) of primes \(\neq 2, p\).
Let \(\ell_0 \in S\). As \(\overline{\rho}_{E_{a,b,c}, p}\) is unramified at \(\ell_0\), 
by Ribet's theorem we find a newform \(f'\) of weight \(2\) and level
\[
    2 \cdot p \cdot \prod_{\ell\in S\setminus\{\ell_0\} \text{ prime}} \ell
\]
such that \(\overline{\rho}_{f'} \cong \overline{\rho}_{E_{a,b,c}, p}\).
By repeating this step, we obtain a newform \(g'\) of weight 2 and level \(2p\) whose reduced 
Galois representation is still equivalent to \(\overline{\rho}_{E_{a,b,c}, p}\). 
As \(\overline{\rho}_{E_{a,b,c}, p}\) is flat at \(p\), 
we find a newform \(g\) of weight \(2\) and level \(2\) such that
\[
    \overline{\rho}_{E_{a,b,c}, p} \cong \overline{\rho}_g.    
\]
However, the only newform of weight \(2\) and level \(2\) is 0, so we obtain the desired contradiction.

\subsection{Wiles' proof: A modularity lifting theorem}
What remains now for the proof of FLT is the proof of the modularity theorem, i.e. that every semistable
elliptic curve is modular.
The goal of this section is to sketch the proof of a theorem that allows us to deduce modularity for
a Galois representation from modularity of its reduction.
In this and in the next section, we follow \cite[chapter 1, \S 7]{Cornell1997}.

Let \(K\) be a finite extension of \(\mathbb{Q}_\ell\) and \(\mathcal{O}\) its ring of integers with residue field \(k\).
Then define the category \(\co\) as the category of local complete noetherian \(\mathcal{O}\)-algebras 
with residue field \(k\) (cf. section 2.2).
Let
\[
    \overline{\rho}\colon G_\mathbb{Q} \to \GL_2(k)
\]
be a reduced Galois representation satisfying the conditions
\begin{enumerate}[(A)]
    \item \(\det \overline{\rho}_{E,p} = \chi_p\)
    \item \(\overline{\rho}_{E,p}\) is semistable
    \item \(\overline{\rho}_{E,p}\) is absolutely irreducible
    \item \(\overline{\rho}_{E,p}\) is modular, and \(\overline{\rho}_{E,p}|_{G_\mathbb{Q}(\sqrt{-3})}\) is absolutely irreducible
\end{enumerate}

The goal of this part of the proof is to show that all \(\overline{\rho}\)-deformations
\[
    \rho\colon G_\mathbb{Q} \to \GL_2(\mathcal{O})
\]
 of type \(\Sigma\) are modular (this is known as modularity lifting).

%deformations in general, deformation types
\begin{definition}\cite[see][chapter 1, paragraph 7.2]{Cornell1997}
We say that a deformation \(\rho\) of \(\overline{\rho}\) is of type \(\Sigma\), if
\begin{itemize}
    \item \(\det \rho = \chi_p\)
    \item \(\rho\) is unramified outside \(S \cup \{p\} \cup \Sigma\) where \(S\) 
    may denote the set of ramified places of \(\overline{\rho}\)
    \item \(\rho\) is semistable outside \(\Sigma\)
    \item if \(p \not \in \Sigma\) and \(\overline{\rho}\) is flat at \(p\), then \(\rho\) is flat at \(p\).
\end{itemize}
\end{definition}

%universal deformation ring
\paragraph{The universal deformation ring}
Consider the functor
\[
    \mathcal{R}_\Sigma \colon \mathcal{C} \to \mathrm{\mathbf{FiniteSets}}  
\]
that sends \(A \in \mathcal{C}\) to the set of deformations of \(\overline{\rho}\) of type \(\Sigma\).
Deformation theory by Mazur tells us that this functor is representable and we 
denote the representing object as \(R_\Sigma\).
Furthermore, we have the existence of a universal representation
\[ 
    \rho_\Sigma^\mathrm{univ}\colon G_\mathbb{Q} \to \GL_2(R_\Sigma).
\]
such that we obtain a 1:1 correspondence
\[
    \hom(R_\Sigma, R) = \left\{\text{deformations } \rho \colon G_\mathbb{Q} \to \GL_2(R) \text{ of type }\Sigma\right\}  
\]
by sending \(\phi \colon R_\Sigma \to R\) to the composition
\(\phi \circ \rho_\Sigma^\mathrm{univ}\colon G_\mathbb{Q} \to \GL_2(R)\).

%Hecke algebra T
Let \(f\) be a cuspidal eigenform \(f\) over \(K\). Regard \(K\) as a subfield of \(\overline{\mathbb{Q}}_\ell\) 
via a fixed embedding \(\overline{\mathbb{Q}} \subset \overline{\mathbb{Q}}_\ell\).
Let the field \(K_f'\) denote the \(K\)-algebra in \(\overline{\mathbb{Q}}_\ell\) generated by
the Fourier coefficients of \(f\) and \(\mathcal{O}_f'\) its ring of integers.
Define
\[
    \tilde{\mathbb{T}}_\Sigma = \prod_{f \in \mathcal{N}_\Sigma} \mathcal{O}_f',
\]
where \(\mathcal{N}_\Sigma\) is a finite set of newforms satisfying certain conditions \cite[see][lemma 3.26]{Darmon1995}.
For all but finitely many primes (e.g. \(p \in \Sigma\) is not allowed), we define
\[
    T_p = (a_p(f))_{f} \in \tilde{\mathbb{T}}_\Sigma.
\]
Finally we can define \(\mathbb{T}_\Sigma\) as the \(\mathcal{O}\)-algebra of \(\tilde{\mathbb{T}}_\Sigma\)
generated by the \(T_p\).
It can be shown \cite[cf.][lemma 3.27]{Darmon1995} that
\[
    \rho_\Sigma^\mathrm{mod} \coloneqq \prod_{f\in \mathcal{N}_\Sigma} \rho_f \colon G_\mathbb{Q} \to \GL_2(\mathbb{T}_\Sigma)
\]
is a Galois representation with the following properties.
\begin{itemize}
    \item \(\rho_\Sigma^\mathrm{mod}\) is a lift of \(\overline{\rho}\) of type \(\Sigma\).
    \item There is a unique surjection \(\phi_\Sigma\colon R_\Sigma \twoheadrightarrow \mathbb{T}_\Sigma\) 
    s.t. \(\rho_\Sigma^\mathrm{mod} \cong \phi_\Sigma \circ \rho_\Sigma^\mathrm{univ}\).
    \item Given a Galois representation \(\rho\colon G_\mathbb{Q} \to \GL_2(\mathcal{O})\) of type \(\Sigma\) and a morphism 
    \[
        \phi \colon \mathbb{T}_\Sigma \to \mathcal{O}
    \]
    s.t. \(\phi \circ \rho^{\mathrm{mod}}_{\Sigma} = \rho\), it follows that \(\rho\) is modular.
\end{itemize}

\paragraph{R = T and the numerical criterion}
In order to show that \(R_\Sigma \cong \mathbb{T}_\Sigma\) for all \(\Sigma\), we need a special argument for
\(\Sigma = \emptyset\). However, from then on we can continue by an induction argument that mainly consists of 
computing the cardinality of some invariants and then applying Wiles' numerical criterion.
This criterion tells us that if a certain inequality is satisfied, the surjection 
\(R_\Sigma \twoheadrightarrow \mathbb{T}_\Sigma\) is an isomorphism (cf. \cref{prop:aimpliesc}).

\paragraph{Proof of modularity lifting}
Consider a representation \(\rho \colon G_\mathbb{Q} \to \GL_2(\mathcal{O})\) and its reduction \(\overline{\rho}\).
Suppose that \(\overline{\rho}\) satisfies properties A - D from \cref{lem:ADproperties}.
By the universal property of \(R_\Sigma\) we get an \(\mathcal{O}\)-algebra morphism \(\phi\) and 
because we know that \(R_\Sigma = \mathbb{T}_\Sigma\), we obtain
\[
    \mathbb{T}_\Sigma \xrightarrow[\sim]{\phi_\Sigma^{-1}} R_\Sigma \xrightarrow{\phi} \mathcal{O}  
\]
s.t. \(\phi \circ \phi_\Sigma^{-1} \circ \rho_\Sigma^\mathrm{mod} = \rho\).
Because of the third property of \(\mathbb{T}_\Sigma\) stated above,
one can now deduce that \(\rho\) must be modular and the modularity lifting theorem follows.

\subsection{Wiles' proof: The 3-5 trick}
In order to finish the proof of the modularity theorem, we now need to show that
the equivalence class of the Galois representation \(\overline{\rho}_{E,p}\) 
associated to an elliptic curve \(E\) is a deformation of type \(\Sigma\) 
of its reduction \(\overline{\rho}\).
\begin{lemma}\label{lem:ADproperties}
    There is a prime \(p\) such that the \(\operatorname{mod} p\) reduction of the galois representation \(\rho_{E,p}\)
    \[
        \overline{\rho}_{E,p} \colon G_\mathbb{Q} \to \GL_2(\mathbb{F}_p)
    \]
    satisfies the following properties.
    \begin{enumerate}[(A)]
        \item \(\det \overline{\rho}_{E,p} = \chi_p\)
        \item \(\overline{\rho}_{E,p}\) is semistable
        \item \(\overline{\rho}_{E,p}\) is absolutely irreducible
        \item \(\overline{\rho}_{E,p}\) is modular, and \(\overline{\rho}_{E,p}|_{G_\mathbb{Q}(\sqrt{-3})}\) is absolutely irreducible
    \end{enumerate}
\end{lemma}
\begin{proof}
    We have seen in \cref{prop:rhoEpproperties} that \(\rho_{E, p}\) has determinant \(\chi_p\). %we need it for the reduction
    As \(E\) is semistable we know that \(\rho_{E, p}\) is semistable. %again, why is this true for the reduction?
    We now need to prove that there is a \(p\) s.t. \(\overline{\rho}_{E,p}\) is irreducible and modular.
    In fact, it can be shown that once irreducibility and modularity are clear, all conditions A-D hold.
    Wiles proved the following
    \begin{proposition}
        Let \(E/\mathbb{Q}\) be a semistable elliptic curve. Then at least one of 
        \(\overline \rho_{E,3}\) or  \(\overline \rho_{E,5}\) is irreducible.
    \end{proposition}%
    This allows us to make a case distinction.
    \begin{itemize}
        \item If \(\overline \rho_{E,3}\) is irreducible, then by some group theoretical considerations 
        we can apply the Langlands-Tunnel-theorem and conclude that \(\overline{\rho}_{E, 3}\) is modular.
        \item If \(\overline \rho_{E,5}\) is irreducible, then Wiles has shown that there is another 
        semistable elliptic curve \(E'/\mathbb{Q}\) s.t. \(\overline{\rho}_{E',3}\) 
        is irreducible and \(\overline{\rho}_{E', 5} \cong \overline{\rho}_{E', 5}\).
        Hence, we can apply the first case for \(E'\) and obtain that \(\overline{\rho}_{E',3}\) is modular.
        However, by modularity lifting \(\rho_{E', 3}\) is modular and by \cref{th:eqcondmodularity}
        then \(\rho_{E', 5}\) is modular. Therefore its reduction \(\overline{\rho}_{E',5}\) and also 
        the equivalent representation \(\overline{\rho}_{E,5}\) are modular.
    \end{itemize}
    In either case we have found a \(p\) s.t. \(\overline{\rho}_{E,p}\) is irreducible and modular.
\end{proof}
By modularity lifting all deformations of type \(\Sigma\) are modular. As the equivalence class of a 
Galois representation associated to a semistable elliptic curve satisfies the conditions required to be of type \(\Sigma\),
we conclude that the Galois representations associated to a semistable elliptic curve is modular.

\newpage

\section{Wiles' numerical criterion}
\subsection{Introduction}
Wiles has discovered a criterion for two rings in a specific category to be isomorphic 
that only depends on some numerical invariants of these rings. 
The aim of this section is to prove that criterion in its purely algebraic form. 
In our presentation, we closely follow \cite[sections 5.1 - 5.8]{Darmon1995}.

\subsection{Preliminaries and examples}
Let \(\mathcal{O}\) be the ring of integers of a finite extension \(K\) of \(\mathbb Q_\ell\). 
As \(K\) is a local field, its ring of integers is a discrete valutation ring (DVR), i.e. 
\(\mathcal O\) is a local, noetherian Dedekind ring with maximal ideal \(\lambda\). 
It is complete with respect to the \(\lambda\)-adic topology, a principal ideal domain (PID) 
and has residue field \(k \coloneqq \mathcal{O}/\lambda\).
\(\mathbb Z_\ell\) is the ring of integers of \(\mathbb Q_\ell\) and 
\(\mathbb F_\ell = \mathbb Z_\ell/\ell \mathbb Z_\ell\) its residue field. 
As \(K/\mathbb{Q}_\ell\) is a finite extension, the residue field \(k\) of \(\mathcal{O}\) 
is a finite extension of $\mathbb F_\ell$ and therefore finite.

\paragraph{The categories \(\co\) and \(\cob\)}
In this section, we will mostly deal with very specific rings. 
Therefore we define the category \(\co\) where objects of \(\co\) are local complete noetherian \(\mathcal O\)-algebras 
with residue field \(k\) and the morphisms are local \(\mathcal{O}\)-algebra morphisms.
Often, we even need some extra structure. 
We obtain the category \(\cob\) from \(\co\) by equipping an object \(A\) 
with an additional surjective \(\mathcal{O}\)-algebra homomorphism
\[\pi_A \colon A \twoheadrightarrow \mathcal{O},\]
the so-called augmentation map. The morphisms in \(\cob\) are local \(\mathcal{O}\)-algebra morphisms 
that respect the augmentation map structure, 
i.e. for a morphism \(f \colon A \to B\) we have the commutative diagram
\[
\begin{tikzcd}[column sep=small]
    A \arrow[rr, "f"] \arrow [dr, "\pi_A", swap, twoheadrightarrow] & & B \arrow [dl, "\pi_B", twoheadrightarrow]\\
    & \mathcal{O} &
\end{tikzcd}.
\]

In order to state Wiles' criterion, we need some more definitions.
\begin{definition}
    \(A \in \co\) is called \textit{finite flat}, if \(A\) is finitely generated 
    and torsion-free as an \(\mathcal{O}\)-module.
    Note that \(\mathcal{O}\) is a PID and therefore being torsion-free 
    is equivalent to being flat as an \(\mathcal{O}\)-module.
\end{definition}

\begin{definition}[complete intersection]\cite[see][Def. 5.1]{Darmon1995}
    A finite flat ring \(A \in \co\) is called a \textit{complete intersection}, 
    if \(A\) is isomorphic as an \(\mathcal{O}\)-algebra to a quotient
    \[A \cong \mathcal{O}[[X_1, \dots, X_n]]/(f_1, \dots, f_n),\] 
    where there are as many relations as there are variables.
    %Why is this a good definition? Where does the name come from? see probably remark 5.2
\end{definition}

Let's take a look at an example.
\begin{example}\label{ex:first_1}\cite[cf.][example 1]{Darmon1995}
    \(A = \{(a,b) \in \mathcal{O}\times\mathcal{O},\; a \equiv b\; (\operatorname{mod} \lambda^n)\} 
    \cong \mathcal{O}[[T]]/(T(T-\lambda^n))\) is a finite flat complete intersection in \(\cob\).
    The projection \(\pi_A\) is given by \(\pi_A(a,b) = a\).
    \begin{proof}
        Consider the map
        \begin{align*}
            \phi\colon \mathcal{O}[[T]]/(T(T-\lambda^n)) &\to A\\
            f &\mapsto (f(0), f(\lambda^n)).
        \end{align*}
        \begin{itemize}
            \item \textbf{\(\phi\) is welldefined and respects the \(\mathcal{O}\)-algebra structure:}
                Let \(f_0\) be the constant term of a polynomial \(f\) and \(f_1 \coloneqq T^{-1}(f-f_0)\), 
                so that \(f = f_0 + T\cdot f_1(T)\). Because of
                \[
                    f(0) - f(\lambda^n) 
                    = (f_0 + 0\cdot f_1(0)) - (f_0 + \lambda^n \cdot f_1(\lambda^n)) 
                    = -\lambda^n \cdot f_1(\lambda^n),
                \]
                \(f(0) \equiv f(\lambda^n)\; (\operatorname{mod} \lambda^n)\) as required.
                Furthermore, \[\phi(T(T-\lambda^n)) = (0(-\lambda^n), \lambda^n(\lambda^n - \lambda^n)) = (0,0).\]
                Also, we need to think about series in \(\mathcal{O}[[T]]\) with infinitely many terms.
                For the first component \(f(0)\) this doesn't matter, as \(\phi\) just takes the constant term. 
                As \(\mathcal{O}\) is complete with respect to the \(\lambda\)-adic topology, 
                the map \(\tilde\phi_2\colon \mathcal{O}[[T]] \to \mathcal{O},\; f \mapsto f(\lambda^n)\) 
                is clearly welldefined and thus \(\phi\) is welldefined.
                %O-algebra structure:
                Let \(o \in \mathcal{O}\). Then 
                \[\phi(of) = (of(0), of(\lambda^n)) = o(f(0), f(\lambda^n)) = o\phi(f)\]
            \item \textbf{Injectivity:}
                Let \(\phi(f) = 0\). Then \(f(0) = 0 \implies T | f\) and \(f(\lambda^n) = 0 \implies (T - \lambda) | f\).
                As a result, \(f \in T(T-\lambda^n)\).
            \item \textbf{Surjectivity:}
                Let \((a,b) \in A\).
                As \(a \equiv b \operatorname{mod} \lambda^n,\) we can write \(b = a + b' \cdot \lambda^n\). 
                Because of
                \[\phi(\overline{a + b'T}) = (a, a + b' \lambda^n) = (a,b),\] 
                \(\phi\) is surjective.
            \item \textbf{\(A\) is finitely generated and torsion-free as an \(\mathcal{O}\)-module:}
                \(A\) is generated by \((1,1)\) and \((0, \lambda^n)\) because
                \[
                    (a,b) = a(1,1) + (0, \underbrace{b-a}_{\in \lambda^n}) = a(1,1) + c(0, \lambda^n),
                \]
                i.e. it's finitely generated as an \(\mathcal{O}\)-module.
                Also, \(A\) is torsion-free because \(\mathcal{O}\) is an integral domain. 
            \item \textbf{\(A\in \cob\):}
                \(\mathcal{O}\) is noetherian, so \(\mathcal{O}[T]/(T(T-\lambda^n))\) is noetherian as well.
                \((\lambda, T)\) is a maximal ideal in \(\mathcal{O}[T]/(T(T-\lambda^n))\), because
                \[\left(\mathcal{O}[T]/(T(T-\lambda^n))\right)/(\lambda, T) = \mathcal{O}/(\lambda) = k.\]
                %this is already complete
                %\(\mathcal{O}[T]/(T(T-\lambda^n))\) is complete with respect to the \(\lambda\)-adic
                %topology because as we have seen it is finitely generated and torsion-free and
                %therefore it's isomorphic to \(\mathcal{O}^2\) as an \(\mathcal{O}\)-module
                %which is \(\lambda\)-complete.
                %Therefore, completing at the maximal ideal \((\lambda, T)\) is 
                %Korollar 24.13 Alg II
                Therefore, the completion \(\mathcal{O}[T]/(T(T-\lambda^n))^{\wedge(\lambda, T)}\) 
                of \(\mathcal{O}[T]/(T(T-\lambda^n))\) with respect to \((\lambda, T)\) is a local ring 
                with maximal ideal \(\widehat{(\lambda, T)}\).
                Consider the SES of finitely generated 
                \textbf{(\(\mathcal{O}[T]\) isn't finitely generated as \(\mathcal{O}\)-module!)} \(\mathcal{O}\)-modules
                \[
                    0 \to (T(T - \lambda^n)) \mathcal{O}[T] \to \mathcal{O}[T] 
                    \to \mathcal{O}[T]/(T(T-\lambda^n)) \to 0.
                \]
                %Theorem 24.9 bzw. see \cite[\href{https://stacks.math.columbia.edu/tag/05D3}{tag 05D3}]{stacks-project}
                As completion of finitely generated \(\mathcal{O}\)-modules is exact 
                (because \(\mathcal{O}\) is noetherian), we get the SES
                \[
                    0 \to (T(T-\lambda^n))\mathcal{O}[[T]] \to \mathcal{O}[[T]] 
                    \to \mathcal{O}[T]/(T(T-\lambda^n))^{\wedge (\lambda, T)}  \to 0.
                \]
                by completing with respect to \((\lambda, T)\).
                As a result, we have
                \[
                    \mathcal{O}[T]/(T(T-\lambda^n))^{\wedge (\lambda, T)} = \mathcal{O}[[T]]/(T(T-\lambda^n)).
                \]
                Hence, \(\mathcal{O}[[T]]/(T(T-\lambda^n))\) is a local ring with maximal ideal \((\lambda, T)\).
                Therefore, its residue field is
                \[
                    \mathcal{O}[[T]]/(T(T-\lambda^n))/(\lambda, T) = \mathcal{O}[T]/(T(T-\lambda^n))/(\lambda, T) 
                    = \mathcal{O}/(\lambda) = k.
                \]
                %Theorem 10.26 in Atiyah-MacDonald
                As \(\mathcal{O}[T]/(T(T-\lambda^n))\) is noetherian, its \((\lambda, T)\)-completion 
                \(\mathcal{O}[[T]]/(T(T-\lambda^n))\) is again noetherian \cite[cf.][theorem 10.26]{Atiyah1969}.
                In total, we get that \(A \cong \mathcal{O}[[T]]/(T(T-\lambda^n))\) is a local, complete, 
                noetherian \(\mathcal{O}\)-algebra with residue field \(k\; \implies A \in \co\).     
        \end{itemize}
        As there is one variable and one relation in \(A \cong \mathcal{O}[[T]]/(T(T-\lambda^n))\) and
        \(A\) is finite flat, it's a complete intersection.
    \end{proof}
\end{example}

%probably add more examples

\begin{example}\label{ex:last_1}\cite[cf.][example 5]{Darmon1995}
    \(U = \mathcal{O}[[X_1, \dots, X_n]]\) with projection \(\pi_U\colon U \to \mathcal{O},\; f \mapsto f(0)\) lies in \(\cob\).
    \begin{proof}
        \(\mathcal{O}\) is noetherian, so \(\mathcal{O}[X_1, \dots, X_{n}]\) is noetherian as well.
        \((\lambda, X_1, \dots, X_n)\) is a maximal ideal in \(\mathcal{O}[X_1, \dots, X_n]\), because
        \[\left(\mathcal{O}[X_1, \dots, X_n]\right)/(\lambda, X_1, \dots, X_n) = \mathcal{O}/(\lambda) = k.\]
        %Korollar 24.13 Alg II
        Therefore, the completion \[\mathcal{O}[X_1, \dots, X_n]^{\wedge(\lambda, X_1, \dots, X_n)} = \mathcal{O}[[X_1, \dots, X_n]]\]
        of \(\mathcal{O}[X_1, \dots, X_n]\) with respect to \((\lambda, X_1, \dots, X_n)\) is a local ring with maximal ideal
        \(\widehat{(\lambda, X_1, \dots, X_n)}\).
        Its residue field is \(\mathcal{O}[X_1, \dots, X_n]/(\lambda, X_1, \dots, X_n) = k\), as required.
        As \(\mathcal{O}[X_1, \dots, X_n]\) is noetherian, its \((\lambda, X_1, \dots, X_n)\)-completion is again noetherian.
    \end{proof}
\end{example}

\begin{remark}\label{rem:quotientofU}
    In \cref{ex:first_1} we could write \(A\) as a quotient of \(\mathcal{O}[[X]]\). 
    This is possible in a more general setting, in fact every \(A \in \cob\) that is 
    finitely generated as an \(\mathcal{O}\)-module
    can be written as a quotient of
    \(U = \mathcal{O}[[X_1, \dots, X_n]]\) for suitable \(n\).
\end{remark}

\begin{proof}
    As \(A\) is a noetherian ring and \(\ker \pi_A\) is an ideal in \(A\), it is finitely generated 
    and therefore also finitely generated as an \(A\)-module.
    As \(A\) is finitely generated as an \(\mathcal{O}\)-module, \(\ker \pi_A\) is also
    finitely generated as an \(\mathcal{O}\)-module. Consider the map
    \begin{align*}
        \Phi\colon U = \mathcal{O}[[X_1, \dots, X_n]] &\to A\\
        X_i &\mapsto a_i,
    \end{align*}
    where \(\ker \pi_A = (a_1, \dots, a_n)\) and \(\pi_U\) is given by \(f \mapsto f(0)\).
    That \(\pi_U\) is welldefined follows from the universal property of the ring of formal power series
    because the target ring \(\mathcal{O}\) is complete.
    As \((X_1, \dots, X_n)\) generate the kernel of \(\pi_U\), this is a map in \(\cob\).
    We have \(A = \mathcal{O} \oplus \ker \pi_A\) because the short exact sequence
    \[
        0 \to \ker \pi_A \to A \to \im \pi_A \cong \mathcal{O} \to 0
    \]
    splits.
    As \(\ker \pi_A\) is generated by the images of \(X_1, \dots, X_n\)
    and \(\mathcal{O}\) is generated by the image of \(1\) over \(\mathcal{O}\), the surjectivity follows immediately
    because \(1, X_1, \dots, X_n \in U\).
    %We have the 
    %and
    %\[
    %    0 \to \ker \pi_U \to U \to \im \pi_U \cong \mathcal{O} \to 0
    %\]
    %As both corresponding sequences split via the inclusion \(\mathcal{O} \hookrightarrow A, x \mapsto x \cdot 1\)
    %resp. \(\mathcal{O} \hookrightarrow U\), we can write \(U \cong \mathcal{O} \oplus \ker \pi_U\) and
    %\(A \cong \mathcal{O} \oplus \ker \pi_A\).
    %\(\Phi\) by definition induces an equality on the first component, 
    %a surjection on the second and therefore is surjective on the direct sum.
\end{proof}

%#Assumption could also be implemented here. Maybe that is even the best idea.
\begin{remark}\label{rem:noconstant}
    For a finite flat complete intersection \(A \in \cob\) we can choose the quotient
    \[
        U \xrightarrow{\alpha} U/(f_1, \dots, f_n) \cong A  
    \]
    in such a way that the augmentation map \(\pi_A\) is induced by 
    \[
        \pi_U\colon \mathcal{O}[[X_1, \dots, X_n]] \to \mathcal{O},\qquad f(X_1, \dots, X_n) \mapsto f(0,\dots, 0).  
    \]
    Because \([f_i] = 0 \; \in A\), necessarily
    \[
        f_i(0) = \pi_U(f_i) = \pi_A(\Phi(f_i)) = \pi_A(0) = 0,  
    \]
    i.e. the relations \(f_i\) must not have a constant term.
\end{remark}
\begin{proof}
    From \cref{rem:quotientofU} we know that we can express \(A\) as a quotient of \(U\),
    \[
        A \cong \mathcal{O}[[X_1, \dots, X_n]]/(\ker \Phi).
    \]
    Considering the definition of \(\Phi\), the statement on \(\pi_A\) follows.
    By \cite[theorem 21.2]{Matsumura1986} it follows that \(\ker \Phi\) can be generated by \(n\) elements.
    Hence we find \(f_1, \dots, f_n\) s.t.
    \[
        A \cong \mathcal{O}[[X_1, \dots, X_n]]/(f_1, \dots, f_n).
    \]
\end{proof}
Note that whenever we write a complete intersection \(A\) as a quotient of \(U\), without loss of generality
we can choose polynomials without constant term and assume that \(\pi_A\) is induced by evaluation at 0 on \(U\).

\begin{definition}
    Let \(A \in \cob\). Then
    \[\phi_A \coloneqq (\ker \pi_A)/(\ker \pi_A)^2.\]
\end{definition}
\begin{lemma}\label{lem:functoriality_phi}
    This assignment is functorial, i.e. for a map \(f\colon A \to B\) in \(\cob\),
    we get a map \(\tilde f\colon \phi_A \to \phi_B\) and this is compatible with
    concatenation of maps.
\end{lemma}
\begin{proof}
    The image of the restriction of \(f\) to \(\ker \phi_A\) is contained in \(\ker \phi_B\), 
    because \(\forall x \in \ker \phi_A\colon\; \pi_B(f(x)) = \pi_A(x) = 0\).
    Concatenating this with the projection to \(\phi_B\), we get a map
    \[
        \tilde f\colon \ker \pi_A \to \ker \pi_B/(\ker \pi_B)^2 = \phi_B.
    \]
    In order to see that \(\tilde f\colon \phi_A \to \phi_B\) is welldefined, we need to show 
    \[
        f(\ker \pi_A)^2 \subset (\ker \pi_B)^2.
    \]
    However, this follows from the fact that \(f(\ker \pi_A) \subset \ker \pi_B\) and that \(f\) is an algebra
    homomorphism:
    \[
        f(x^2) = \underbrace{f(x)}_{\in \ker \pi_B}\underbrace{f(x)}_{\in \ker \pi_B} \in (\ker \pi_B)^2 
    \]
    for any \(x \in \ker \pi_A\).
    We don't show the compatibilty with concatenation here, but we also won't use in the following.
\end{proof}

\begin{example}\label{ex:last_phi}
    Remember the definition of \(U\) in \cref{ex:last_1}.
    The tangent space \(\phi_U = \ker \pi_U/(\ker \pi_U)^2\) is
    \[
        \mathcal{O}X_1 \oplus \dots \oplus \mathcal{O}X_n.
    \]
    Indeed, elements of \(f \in \ker \pi_U\) have no constant term as \(f(0) = 0\) and therefore are multiples of \(X\).
    Elements in \(\ker \pi_U^2\) are multiples of \(X^2\). As a result, we receive elements \(\overline{f} \in \phi_U\) by
    cutting of all higher terms of a power series \(f \in \ker \pi_U\).
\end{example}

\begin{remark}\label{rem:tangentspace}
    Write \(A\) as a quotient of \(U,\; A = U/(f_1, \dots, f_m)\). 
    This is possible because of \cref{rem:quotientofU}.
    We then get \(\phi_A = \phi_U/(\overline{f_1}, \dots, \overline{f_m})\).
    As a quotient of \(\phi_U\) its a finitely generated \(\mathcal{O}\)-module.
\end{remark}
\begin{proof}
    Consider the following map of \(\mathcal{O}\)-modules
    %\begin{align*}
    %    \Phi\colon \ker \pi_U = \mathcal{O}X_1 \oplus \dots \oplus \mathcal{O}X_n &\to (\ker \pi_A)/(\ker \pi_A)^2 = \phi_A\\
    %    a_1X_1 + \dots + a_nX_n &\mapsto [a_1X_1 + \dots + a_nX_n] \; \mod (\ker \pi_A)^2,
    %\end{align*}
    \begin{align*}
        \Phi\colon \ker \pi_U &\to (\ker \pi_A)/(\ker \pi_A)^2 = \phi_A\\
        f &\mapsto [f] \; \mod (\ker \pi_A)^2,
    \end{align*}
    where \([f]\) denotes the image of \(f\) in \(A\).
    Then, as \(\pi_A([f]) = f(0)\), we get that \(X_i \in \ker \pi_A \forall i\)
    and therefore \([f] \in \ker \pi_A \forall f \in \ker \pi_U\). Not only is \(\Phi\) welldefined,
    we can conclude that \(X_i \in \ker \pi_A \implies X_i^2 \in (\ker \pi_A)^2\)
    and therefore \(\Phi\) is also surjective and \((\ker \pi_U)^2 \subset \ker \Phi\).
    
    With this knowledge we get a welldefined surjective map
    \begin{align*}
        \tilde \Phi\colon \phi_U = \mathcal{O}X_1 \oplus \dots \oplus \mathcal{O}X_n &\to \phi_A\\
        a_1X_1 + \dots + a_nX_n \; \mod (\ker \pi_U)^2 &\mapsto [a_1X_1 + \dots + a_nX_n] \; \mod (\ker \pi_A)^2.
    \end{align*}
    Elements in the kernel of this map are either generated by \(X_i^2\) so they vanish modulo \((\ker \pi_A)^2\)
    or they become 0 by sending them to \(A = U/(f_i)\).
    As higher order terms of \(f_i\) are vanishing anyways, 
    the kernel of \(\tilde \Phi\) is generated by the \(\overline{f_i}\), i.e.
    \[
        \phi_A \cong \phi_U/(\overline{f_i})  
    \]
\end{proof}

\begin{example}\label{ex:first_phi}
    We now compute \(\phi_A\) where \(A\) was defined in \cref{ex:first_1}.
    Remember that \(f = T(T-\lambda^n) = -\lambda^n T + T^2\). Therefore,
    \[\phi_A = \mathcal{O}T/(-\lambda^n T) = \mathcal{O}/\lambda^n.\]
\end{example}

\begin{definition}
    Let \(A \in \cob\). Then
    \[\eta_A \coloneqq \pi_A(\ann_A (\ker \pi_A))\] is an ideal in \(\mathcal{O}\).
\end{definition}

\begin{example}
    We now compute \(\eta_U\) for \(U\) from \cref{ex:last_1}.
    \begin{align*}
        \eta_U &= \pi_U(\ann \ker \pi_U)\\
        &= \pi_U(\ann \mathcal{O}X_1 \oplus \dots \oplus \mathcal{O}X_n)\\
        &= \pi_U(0) = 0.
    \end{align*}
\end{example}

\begin{lemma}\label{lem:ideals}
    Let \(\mathfrak a \subset \mathcal{O}\) be an ideal. Then
    \[\mathfrak a \neq 0 \implies \mathcal{O}/\mathfrak a \text{ finite}.\]
\end{lemma}
\begin{proof}
    As \(\mathcal{O}\) is a DVR, \(\mathfrak a = \lambda^n\) for some \(n \in \mathbb N\) 
    where \(\lambda\) is the maximal ideal in \(\mathcal{O}\).
    Therefore, \(\mathcal{O}/\mathfrak{a} = \mathcal{O}/\lambda^n.\)

    Using the fact that \(\lambda = (t)\) for some uniformizer \(t\), we get \(\forall i \ge 1\) 
    the isomorphism \(\lambda^i/\lambda^{i+1} \cong \mathcal{O}/\lambda = k\) and thereby also the short exact sequence 
    \[0 \to \mathcal{O}/\lambda \cong \lambda^i/\lambda^{i+1} \to \mathcal{O}/\lambda^{i+1} \to \mathcal{O}/\lambda^{i} \to 0.\]
    As \(k = \mathcal{O}/\lambda\) is finite, we can use induction
    \[\# \mathcal{O}/\lambda^{i+1} = \# \mathcal{O}/\lambda \cdot \# \mathcal{O}/\lambda^i = \# k \cdot (\# k)^i = (\# k)^{i+1}\]
    and get \(\# \mathcal{O}/\mathfrak{a} = \# \mathcal{O}/\lambda^n = (\# k)^n\).
\end{proof}

\begin{example}\label{ex:first_eta}
    We now compute \(\eta_A\) for \(A\) from \cref{ex:first_1}.
    \begin{align*}
        \eta_A &= \pi_A(\ann \ker \pi_A)\\
        &= \pi_A(\ann \{(0, b) \subset \mathcal{O}\times \mathcal{O} | b \equiv 0 \mod \lambda^n\})\\
        &= \pi_A(\{(a, 0) \subset \mathcal{O}\times \mathcal{O} | a \equiv 0 \mod \lambda^n\})\\
        &= \pi_A((\lambda^n) \times 0)\\
        &= (\lambda^n)
    \end{align*}
\end{example}

\begin{example}\label{ex:ddt3}\cite[cf.][example 3]{Darmon1995}
    \(A = \mathcal{O}[[X]]/(X^2)\) with augmentation \(\pi_A\colon A \to \mathcal{O},\; f \mapsto f(0)\) 
    is a finite flat complete intersection in \(\cob\).
    Furthermore, \(\phi_A = \mathcal{O}\) and \(\eta_A = 0\).
\end{example}
\begin{proof}
    \(A \in \cob\) is analogous to \cref{ex:first_1}. 
    \[
        \phi_A = \phi_U/(\overline{X^2}) = \mathcal{O}X/(0) \cong \mathcal{O}
    \] 
    and
    \[
        \pi_A(\ann_A \ker \pi_A) = \pi_A(\ann_A X \mathcal{O}[[X]]) = \pi_A(X \mathcal{O}[[X]]) = (0).  
    \]
\end{proof}

\begin{example}\label{ex:ddt2}\cite[section 5.1, example 2]{Darmon1995}
    \[
        A = \{(a, b, c) \in \mathcal{O}^3, a \equiv b \equiv c \mod \lambda\}
    \]
    is finite flat and element of \(\cob\) with augmentation \(\pi_A(a, b, c) \coloneqq a\).
    Furthermore, 
    \[
        \phi_A \cong \mathcal{O}/\lambda \mathcal{O} \times \mathcal{O}/\lambda \mathcal{O},\quad \eta_A = (\lambda)
    \]
\end{example}
\begin{proof}
    One can show that 
    \[
       \mathcal{O}[[X, Y ]]/(X(X - \lambda), Y (Y - \lambda), XY) \cong A
    \]
    via \(f \mapsto (f(0,\lambda), f(\lambda, 0), f(0,0))\).
    Then \(\phi_A\) is easy to compute. \(\eta_A\) is computed analogous to \cref{ex:first_eta}.
\end{proof}

\begin{example}\label{ex:ddt4}\cite[section 5.1, example 4]{Darmon1995}
    \[
        A = \{(a, b, c, d) \in \mathcal{O}^4, a \equiv b \equiv c \equiv d \mod \lambda, 
        a + d \equiv b + c \mod \lambda^2\}
    \]
    is finite flat and element of \(\cob\) with augmentation \(\pi_A(a, b, c) \coloneqq a\).
    Furthermore,
    \[
        \phi_A \cong \mathcal{O}/\lambda \mathcal{O} \times \mathcal{O}/\lambda \mathcal{O}, \eta_A = (\lambda^2)
    \]
\end{example}
\begin{proof}
    One can show that 
    \[
        \mathcal{O}[[X, Y]]/(X(X - \lambda), Y (Y - \lambda)) \cong A
    \]
    via \(f \mapsto (f(0,0), f(0, \lambda), f(\lambda, 0), f(\lambda, \lambda))\).
    Then \(\phi_A\) is easy to compute and
    \begin{multline*}
        \eta_A = \pi_A(\ann_A\ker\pi_A) = \pi_A(\ann_A \{(0,b,c,d) \in A\}) \\
        = \pi_A(\{(a,0,0,0) \in \mathcal{O}^4, a \equiv 0 \mod \lambda^2\}) = \lambda^2
    \end{multline*}
\end{proof}

After these examples we now state Wiles' numerical criterion.
\begin{theorem}\textup{\cite[theorem 5.3]{Darmon1995}}\label{thm:wiles_numerical_criterion}
    Let \(R \twoheadrightarrow T\) a surjective morphism in \(\cob\), \(T\) finite flat and \(\eta_T \neq 0\) 
    (i.e. \(\mathcal{O}/\eta_T\) finite).
    Then the following are equivalent.
    \begin{enumerate}[(a)]
        \item \(\# \phi_R \le \#(\mathcal{O}/\eta_T)\),
        \item \(\# \phi_R = \#(\mathcal{O}/\eta_T)\),
        \item \(R\) and \(T\) are complete intersections, and \(R \to T\) is an isomorphism.
    \end{enumerate}
\end{theorem}

\subsection{Basic properties of the invariants}
In this subsection we prove the equivalence (a) \(\Leftrightarrow\) (b) in \cref{thm:wiles_numerical_criterion}
by investigating the invariants \(\phi_A\) and \(\eta_A\) that we defined last section.

\begin{lemma}\label{lem:surjectivity_phi}
    For a morphism \(f\colon A \to B \in \cob\), by functoriality (\cref{lem:functoriality_phi}) we
    have an induced homomorphism \(\tilde f\colon\phi_A \to \phi_B\) of \(\mathcal{O}\)-modules.
    \(f\) is surjective if and only if \(\tilde f\) is surjective.
\end{lemma}
For the 'if'-part, see \cites[lemma 5.5]{Darmon1995}[theorem 8.4]{Matsumura1986}%
[ch. II, lemma 7.4]{Hartshorne1977}[\href{https://stacks.math.columbia.edu/tag/090T}{tag 090T}]{stacks-project}.
\begin{proof}
    First, let us assume that \(f\colon A \to B\) is a surjective map.
    In this case, every element \(x \in \ker \phi_B\) has a preimage in \(\ker \pi_A\). 
    Indeed, \(\forall y \in f^{-1}(x)\subset A\colon\)
    \[
        \pi_A(y) = \pi_B(f(y)) = \pi_B(x) = 0.
    \]
    As a result, the induced map \(f\colon \ker \pi_A \to \ker \pi_B\) and its concatenation with
    the projection to \(\phi_B\), \(\tilde f\colon \ker \pi_A \to \ker \pi_B/(\ker \pi_B)^2\) are both surjective.
    In total, we obtain a surjective homomorphism \(\tilde f\colon \phi_A \to \phi_B\).
    
    Now, let \(\tilde f\colon \phi_A \to \phi_B\) be surjective. 
    Consider the ideal \(I = f(\ker \pi_A) \cdot B\) in \(B\).
    Let \(x \in I\). Then \(x = \sum_i f(x_i) \cdot b_i\) for \(x_i \in \ker \pi_A\) and \(b_i \in B\).
    We have the commutative diagram
    \[
    \begin{tikzcd}[column sep=small]
        A \arrow[rr, "f"] \arrow [dr, "\pi_A", swap, twoheadrightarrow] & & B \arrow [dl, "\pi_B", twoheadrightarrow]\\
        & \mathcal{O} &
    \end{tikzcd}.
    \]
    Therefore,
    \[
        \pi_B(x) = \pi_B\left(\sum_i f(x_i)\cdot b_i\right) 
        = \sum_i \pi_B(f(x_i))\cdot \pi_B(b_i) 
        = \sum_i\pi_A(x_i)\cdot \pi_B(b_i) = 0. 
    \]
    As a result, \(I \subset \ker \pi_B \subset \mathfrak{m}_B\).
    Note that
    \[
        f(\ker \pi_A) \subset f(\ker \pi_A)\cdot B \implies f((\ker \pi_A)^n) 
        = f(\ker \pi_A)^n \subset (f(\ker \pi_A)\cdot B)^n,
    \]
    so we have \(f((\ker \pi_A)^n)\cdot B \subset I^n\).
    As \(B\) is \(\mathfrak{m}_B\)-adically complete and therefore Hausdorff, we get
    \[
        \bigcap_{n \in \mathbb N} f((\ker \pi_A)^n) \cdot B \subset \bigcap_{n \in \mathbb N} I^n 
        \subset \bigcap_{n \in \mathbb N} \mathfrak{m}_b^n = 0,
    \]
    i.e. \(\!B\) is separated with respect to the \(I\)-adic topology.
    Furthermore, \(\ker \pi_A\) is finitely generated as an \(A\)-module, 
    \(\ker \pi_A = \langle a_1, \dots, a_m\rangle\) because \(A\) is noetherian. 
    As \(\ker \pi_A \to (\ker \pi_B)/(\ker \pi_B)^2\) is surjective, we have 
    \[(\ker \pi_B)/(\ker \pi_B)^2 = \langle \overline{f(a_1)}, \dots, \overline{f(a_m)}\rangle_B.\]
    As \(A\) is \(\mathfrak{m}_A\)-adically complete, \(\ker \pi_A\) is finitely generated as an \(A\)-module
    and \(\ker \pi_A \subset \mathfrak{m}_A\), \(A\) is \(\ker \pi_A\)-adically complete as well
    \cite[cf.][\href{https://stacks.math.columbia.edu/tag/090T}{tag 090T}]{stacks-project}.
    Furthermore, \(I\) is separated with respect to the \(I\)-adic topology 
    as a submodule of \(B\). Together with the fact that \(A\) is \(\ker \pi_A\)-adically complete,
    we can apply Nakayama's Lemma as in Mat, 8.4. 
    It follows that the images \(\langle f(a_1), \dots, f(a_m)\rangle\) generate \(\ker \pi_B\)
    as a \(B\)-module. We already know that \(f(\ker \pi_A) \cdot B \subset \ker \pi_B\). 
    In total we have
    \[
        f(\ker \pi_A) \cdot B = \ker \pi_B.
    \]
    Now we conclude that \(1\) is a generator of \(B/I = B/f(\ker \pi_A) B = B/\ker \pi_B = \mathcal{O}\) as an 
    \(A/\ker \pi_A \cong \mathcal{O}\)-module.
    Applying Nakayama's Lemma again, we get that \(1\) is a generator of \(B\) as an \(A\)-module 
    and hence, \(f\colon A \to B\) is surjective.
\end{proof}

\begin{corollary}\label{cor:surjectivity_phi}
    Let \(A, B\in \cob\) and \(\phi_A\) be finite. %Then \(\phi_B\) is finite as well
    If \(A \to B\) is surjective, then \[\# \phi_A \geq \# \phi_B.\]
\end{corollary}

\begin{lemma}\label{lem:surjectivity_eta}
    If \(f \colon A \to B\) is surjective, then
    \begin{equation*}
        \eta_A \subset \eta_B, \quad \text{i.e. if \(\eta_A \neq 0\),}\quad \#(\mathcal{O}/\eta_A) \geq \#(\mathcal{O}/\eta_B).  
    \end{equation*}
\end{lemma}
\begin{proof}
    As we have seen in the proof of \cref{lem:surjectivity_phi}, a surjective map \(f\) induces a surjective
    map on the kernels, \(f\colon \ker \pi_A \to \ker\pi_B\).
    Now let \(x \in \ann_A \ker \pi_A\), i.e. \(x \cdot a = 0\;\; \forall a \in \ker \pi_A\).
    For all \(b \in \ker \pi_B\) and any preimage \(a \in \ker \pi_A\) we have
    \[
        f(x) \cdot b = f(x) \cdot f(a) = f(x \cdot a) = f(0) = 0.
    \]
    As a result, \(f(x) \in \ann_B\ker \pi_B\) and we obtain a map
    \[
        \tilde f\colon\ann_A\ker \pi_A \to \ann_B \ker \pi_B.  
    \]
    In order to show \(\eta_A \subset \eta_B\), let \(x \in \eta_A = \pi_A(\ann_A \ker \pi_A)\), i.e.
    \(x = \pi_A(y)\) for some \(y \in \ann_A \ker \pi_A\). By the commutative diagram
    \[
    \begin{tikzcd}[column sep=small]
        \ann_A \ker \pi_A \arrow[rr, "\tilde f"] \arrow [dr, "\pi_A", swap, twoheadrightarrow] 
        & & \ann_B \ker \pi_B \arrow [dl, "\pi_B", twoheadrightarrow]\\
        & \mathcal{O} &
    \end{tikzcd},
    \]
    we get
    \[
        x = \pi_A(y) = \pi_B(\tilde f(y)) \in \pi_B(\ann_B \ker \pi_B) \implies x \in \eta_B,
    \]
    as desired.
\end{proof}

\begin{definition}
    Let \(M\) be a finitely generated \(R\)-module. Then \(M\) is a quotient
    \[
        P \colon R^n \longrightarrow M = R^n/\ker P
    \]
    We define \(\fitt_R(M) \coloneqq \langle \det(v_1, \dots, v_n) | v_i \in \ker P \rangle_R \subset R\).
    This is independent of the choice of the surjection 
    (see e.g. \cite[\href{https://stacks.math.columbia.edu/tag/07Z6}{tag 07Z6}]{stacks-project}).
\end{definition}

\begin{lemma}\label{lem:fitting_and_ann}
    For a finitely generated \(R\)-module \(M\) we have
    \[\fitt_R(M) \subset \ann_R(M).\]
\end{lemma}
\begin{proof}
    \(M\) is generated by the residue classes of the canonical basis of \(R^n\),
    \[
        M = \langle \overline{e_1}, \dots, \overline{e_n}\rangle_R    
    \]
    where \(\overline{x}\) may denote the residue class of \(x \mod \ker P\).
    Now let \([v_1|\dots|v_n]\) be a matrix with \(v_i \in \ker P\). Then this matrix annihilates \(M\) because
    it annihilates all the generators \(\overline{e_i}\),
    \[
        [v_1|\dots|v_n] \cdot e_i = v_i \in \ker P.
    \]
    Let \(A\) be the adjugate matrix of \([v_1|\dots|v_n]\), i.e. \[A[v_1|\dots|v_n] = \det [v_1|\dots|v_n]\cdot I_{n\times n}.\]
    Let \(m \in M\) and \((m_i)_{i=1}^n\) a lift in \(R^n\). Then we have 
    \begin{align*}
        \det [v_1|\dots|v_n] \cdot m &= \det [v_1|\dots|v_n]\cdot I_{n\times n} (m_i)_{i=1}^n \\
        &= A[v_1|\dots|v_n]\left(\sum_{i=1}^n m_i e_i\right)\\
        &= A \cdot \sum_{i=1}^n m_i v_i \in A \cdot \ker P \subset \ker P
    \end{align*}
    Therefore \(\fitt_R(M) \subset \ann_R(M)\).
\end{proof}

\begin{remark}[Fitting ideals and \(\otimes\)]\label{rem:fitting_and_tensor}
    Let \(A \in \cob\) and \(M\) a finitely generated \(A\)-module. 
    Note that \(\mathcal{O}\) has an \(A\)-module structure via \(\pi_A\).
    We have
    \[
        \pi_A(\fitt_A(M)) = \fitt_\mathcal{O}(M \otimes_A \mathcal{O}).
    \]
    This follows from the fact that \(- \otimes_A \mathcal{O}\) is right exact. 
    Hence, from the exact sequence
    \[
        \ker P \longrightarrow A^n \longrightarrow M \longrightarrow 0
    \]
    we get the exact sequence
    \[
        \ker P \otimes_A \mathcal{O} \longrightarrow A^n\otimes_A \mathcal{O} = \mathcal{O}^n 
        \longrightarrow M\otimes_A \mathcal{O} \longrightarrow 0.
    \]
    The remaining details are left as an exercise to the reader.
\end{remark}

\begin{remark}[Fitting ideals for finitely generated \(O\)-modules]
    Let \(M\) be a finitely generated \(O\)-module. As \(O\) is a PID, there are unique \(r,s \in \mathbb{N}\) 
    and \(n_1 \geq \dots \geq n_s \in \mathbb{N}\) s.t.
    \[
        M = \mathcal{O}^r \oplus \mathcal{O}/\lambda^{n_1} \oplus \dots \oplus \mathcal{O}/\lambda^{n_s}.
    \]
    If \(r > 0\), then every \(v \in \ker P \subset \mathcal{O}^{r + s}\) has \(r\) zero components.
    Therefore, \(\fitt_R (M) = 0\) for \(r > 0\).
    If \(r = 0\), the \(i\)-th component of \(v \in \ker P \subset \mathcal{O}^s\) 
    lies in the kernel of \(\mathcal{O} \to \mathcal{O}/\lambda^{n_i}\), 
    i.e. \(v_i \in \lambda^{n_i}\).
    Using the Leibniz formula for computing the determinant, we get
    \(\fitt_\mathcal{O}(M) = \lambda^{n_1} \cdot \dots \cdot \lambda^{n_s} = \lambda^{n_1 + \dots + n_s}\).
\end{remark}

\begin{corollary}\label{cor:fitting_finite}
    Let \(M\) be a finite \(\mathcal{O}\)-module. Then
    \[
        \# M = \# (\mathcal{O}/\fitt_\mathcal{O}(M)). 
    \]
\end{corollary}
\begin{proof}
    As \(M\) is finite, we get
    \[
        M = \mathcal{O}/\lambda^{n_1} \oplus \dots \oplus \mathcal{O}/\lambda^{n_s}
    \]
    and 
    \[
        \fitt_\mathcal{O}(M) = \lambda^{n_1 + \dots + n_s}.
    \]
    From the proof of \cref{lem:ideals} it follows that
    \[\# M = (\# k)^{n_1} \cdot \dots \cdot (\# k)^{n_s} = (\# k)^{n_1 + \dots + n_s}\]
    and
    \[
        \# (\mathcal{O}/\fitt_\mathcal{O}(M)) = \# (\mathcal{O}/\lambda^{n_1 + \dots + n_s}) = (\# k)^{n_1 + \dots + n_s}.
    \]
\end{proof}

\begin{lemma}\label{lem:standard_ineq}
    Let \(A \in \cob\) s.t. \(\phi_A\) finite and \(\eta_A \neq 0\). Then \[\#\phi_A \geq \#(\mathcal{O}/\eta_A).\]
\end{lemma}
\begin{proof}
    As \(\mathcal{O} = A/\ker \pi_A\), we have
    \[
        \ker \pi_A \otimes_A \mathcal{O} = \ker \pi_A \otimes_A A/\ker \pi_A \cong \ker \pi_A/(\ker \pi_A)^2 = \phi_A.
    \]
    We therefore have
    \[
        \fitt_\mathcal{O}(\phi_A) = \fitt_\mathcal{O}(\ker \pi_A \otimes_A\mathcal{O}) = \pi_A(\fitt_A(\ker \pi_A))
    \]
    where the second equality follows from \cref{rem:fitting_and_tensor}.
    Applying \cref{lem:fitting_and_ann}, we get
    \[
        \fitt_\mathcal{O}(\phi_A) \subset \pi_A(\ann_A(\ker \pi_A)) = \eta_A.
    \]
    As \(\phi_A\) is finite, we can apply \cref{cor:fitting_finite} to \(M = \phi_A\) and obtain
    \[
        \# \phi_A = \# (\mathcal{O}/\fitt_\mathcal{O}(\phi_A)) \geq \# (\mathcal{O}/\eta_A).
    \]
\end{proof}

\begin{proposition}\textup{\cite[cf.][corollary 5.6]{Darmon1995}}\label{prop:aequalsb}
    (a) \(\Leftrightarrow\) (b) in \cref{thm:wiles_numerical_criterion}.
\end{proposition}
\begin{proof}
    By assumption, \(R \to T\) is a surjective morphism in \(\cob\).
    With \cref{cor:surjectivity_phi} it follows that \(\#\phi_R \geq \#\phi_T\). \Cref{lem:standard_ineq} 
    tells us that \(\#\phi_T \geq \#(\mathcal{O}/\eta_T)\).
    The inequalities combine to \[\#\phi_R \geq \#(\mathcal{O}/\eta_T).\]
    In both cases the finiteness of \(\mathcal{O}/\eta_T\) implies the finiteness of \(\phi_R\)
    and from that we obtain the finiteness of \(\#\phi_T\).
    (a) gives us \(\#\phi_R \leq \#(\mathcal{O}/\eta_T)\), so combined with \(\#\phi_R \geq \#(\mathcal{O}/\eta_T)\) 
    we conclude that (b) must hold. (b) \(\implies\) (a) is clear.
\end{proof}

\subsection{Regular sequences and the Koszul complex}
Let \(A\) be a finite flat complete intersection. Hence we can write 
\[A = \mathcal{O}[[X_1, \dots, X_n]]/(f_1, \dots, f_n).\]
The goal of this section is to prove some technical lemmata and to introduce
the Koszul complex that we will use to construct two \(\mathcal{O}[[X]]\)-free resolutions for \(A\).
This will turn out to be crucial in the next section.

We start with a few definitions from commutative algebra, closely following \cite[section 5.3]{Darmon1995}
\begin{definition}[primary ideal]
    Let \(R\) be a local ring and \(\mathfrak{a} \subsetneq R\) an ideal. 
    \(\mathfrak{a}\) is said to be primary if every zero divisor in \(R/\mathfrak{a}\) is nilpotent.
\end{definition}
Recall that the dimension of a ring is given by
\[
    \sup \left\{n | 
                \mathfrak{p}_0 \subsetneq \dots \subsetneq \mathfrak{p}_n \subsetneq R,\; \mathfrak{p}_i \text{ prime} 
        \right\}.
\]
\begin{definition}[system of parameters]
    Let \(x_1, \dots, x_n\) generate a primary ideal of \(R\). If \(n = \dim R\) then \(x_1, \dots, x_n\) is called 
    a system of parameters.
\end{definition}

\begin{lemma}\label{lem:sys_params}\textup{\cite[lemma 5.10]{Darmon1995}}
    The sequence \((f_1, \dots, f_n, \lambda)\) is a system of parameters for \(U\) (cf. \cref{ex:last_1}).
\end{lemma}
\begin{proof}
    First, we show that \(\dim U = n + 1\).
    We have an ascending chain of prime ideals
    \[
        (0) \subsetneq (\lambda) \subsetneq \dots \subsetneq (\lambda, X_1, \dots, X_n),  
    \]
    so by definition of the dimension we get 
    \begin{equation}
        \dim U \geq n + 1.\label{eq:gnp1}
    \end{equation}
    %Corollary 26.18 of Prof. Schmidt's Algebra script
    Let \(\mathfrak{m} = (\lambda, X_1, \dots, X_n)\). We have seen that this is the maximal ideal in \(U\).
    Using \cite[corollary 11.15]{Atiyah1969}, we can conclude 
    \[
        \dim U \leq \dim_{U/\mathfrak{m}}(\mathfrak{m}/\mathfrak{m}^2) 
        = \dim_k(\lambda/\lambda^2 \oplus k X_1 \oplus \dots \oplus k X_n).
    \]
    As \(\lambda/\lambda^2 \cong k\) (cf. \cref{lem:ideals}), the above expression evaluates to \(n+1\) and we have
    \begin{equation}
        \dim U \leq n + 1.\label{eq:lnp1}
    \end{equation}
    Taking the inequalities \ref{eq:gnp1} and \ref{eq:lnp1} together, we obtain \(\dim U = n + 1\).
    It remains to show that \((f_1, \dots, f_n, \lambda)\) generate a primary ideal of \(U\).
    \(U\) is local and therefore the quotient ring 
    \[\tilde{U} \coloneqq U/(f_1, \dots, f_n, \lambda)\] 
    is local as well.
    Also, \(\tilde U\) is a \(k\)-vector space (because it's an \(\mathcal{O}\)-module and \(\lambda\)-operation
    annihilates it). As \(A = U/(f_1, \dots, f_n)\) is a finitely generated \(\mathcal{O}\)-module, we can find
    \((x_1, \dots, x_N)\) that generate \(A\) as \(\mathcal{O}\)-module.
    These \(x_i\) then generate \(\tilde U\) as a \(k\)-vector space.
    As \(k\) is finite, the whole vector space is finite.
    As a result, the chain of powers of \(\mathfrak{m}_{\tilde U}\) must stabilize,
    \[
        \mathfrak{m}_{\tilde U}^n = \mathfrak{m}_{\tilde U}^{n+1}
    \]
    By Nakayama's lemma it follows that \(\mathfrak{m}_{\tilde U}^n = 0\).
    Hence, every element of the maximal ideal is nilpotent.
    As zero-divisors are never units, they are contained in the maximal ideal and, a fortiori, nilpotent.
    In total, \(f_1, \dots, f_n, \lambda\) generate a primary ideal of \(U\).
\end{proof}

\begin{definition}[regular sequence]\cite[cf.][definition 1.1.1]{Bruns1998}
    A sequence \((x_1, \dots, x_n)\) is said to be a regular sequence 
    if \(\forall\; i = 1, \dots, n\colon\)
    \[x_i \text{ is not a zero-divisor in } R/(x_1, \dots, x_{i-1}).\]
\end{definition}

\begin{theorem}\cite[theorem 1.2.5]{Bruns1998}
    Let \(R\) be a local noetherian ring with maximal ideal \(\mathfrak{m}\).
    A regular sequence \((x_1, \dots, x_n)\) is maximal, if \((x_1, \dots, x_{n+1})\)
    is not regular for any \(x_{n+1} \in \mathfrak{m}\).
    All maximal regular sequences have the same length.
\end{theorem}

\begin{definition}[depth]\cite[definition 1.2.6, 1.2.7]{Bruns1998}
    The depth of a local noetherian ring \(R\) with maximal ideal \(\mathfrak{m}\) is 
    defined as the length of a (any) maximal regular sequence in \(\mathfrak{m}\).
\end{definition}

\begin{definition}[Cohen-Macaulay]
    A local ring \(R\) is called Cohen-Macaulay if 
    \[
        \operatorname{depth} R = \operatorname{dim} R.  
    \]
\end{definition}

\begin{lemma}\label{lem:reg_seq}\textup{\cite[lemma 5.11]{Darmon1995}}
    The sequence \((f_1, \dots, f_n)\) is a regular sequence for \(U\).
\end{lemma}
\begin{proof}
    The sequence \((\lambda, X_1, \dots, X_n)\) is a regular sequence for \(U\) because
    \(U/\lambda = k[[X_1, \dots, X_n]]\) and \(U/(\lambda, X_1, \dots, X_{i-1}) = k[[X_i, \dots, X_n]]\) 
    are integral domains (hence obviously \(X_i\) can't be a zero-divisor in these rings).
    As we have seen in the previous lemma, it's as well a system of parameters.
    Therefore, the depth of \(U\) (i.e. the maximal length of any regular sequence in \(U\)) is bigger than
    the length of the particular regular sequence \((\lambda, X_1, \dots, X_n)\).
    In total we get \(\operatorname{depth} U \geq \dim U\), because \((\lambda, X_1, \dots, X_n)\) 
    is a system of parameters as well.
    %source?
    In general, we have \(\operatorname{depth} R \leq \dim R\) for a noetherian local ring \(R\), 
    so combined we have
    \[
        \operatorname{depth} U = \dim U  
    \]
    and hence, \(U\) is Cohen-Macaulay.
    %Matsumura, Theorem 17.4
    As \((f_1, \dots, f_n, \lambda)\) is a system of parameters and \(U\) is Cohen-Macaulay
    it follows that \((f_1, \dots, f_n, \lambda)\) is a regular sequence \cite[theorem 17.4]{Matsumura1986}.
    A fortiori, the sequence \((f_1, \dots, f_n)\) is also a regular sequence.
\end{proof}

\begin{corollary}\textup{\cite[corollary 5.12]{Darmon1995}}\label{cor:flatness}
    Let \(A \in \cob\) be finitely generated as an \(\mathcal{O}\)-module and of the form
    \[
        A \cong \mathcal{O}[[X_1, \dots, X_n]]/(f_1, \dots, f_n).  
    \]
    Then \(A\) is flat.
\end{corollary}
\begin{proof}
    In the proof of \cref{lem:sys_params} we have never used that \(A\) is flat, 
    only that it is finitely generated as an \(\mathcal{O}\)-module. Therefore we know that \(f_1, \dots, f_n, \lambda\) is a system of parameters
    for \(U\).
    From the proof of \cref{lem:reg_seq} (where we also haven't used that \(A\) is flat) we can deduce that
    \(f_1, \dots, f_n, \lambda\) is also a regular sequence for \(U\) and, a fortiori, \(\lambda\) is not a 
    zero-divisor in \(U/(f_1, \dots, f_n) = A\).
    Assume that \(A\) is not flat, i.e. there is a \(\lambda^m u \in \mathcal{O}\) and a
    \[0 \neq g(X_1, \dots, X_n) \in A \qquad \text{s.t. } \lambda^m u \cdot g(\underline{X}) = 0.\]
    Consider \(g' = \lambda^{m-1}u g\). If \(g'\) is still zero, define \(g''\coloneqq \lambda^{m-2}u g\) etc.
    After finitely many steps we find a \(0 \neq g \in A\) s.t. \(\lambda g = 0\), contradiction.
\end{proof}

%The Koszul complex
\begin{definition}[Koszul complex]\cites[ch. 5.3]{Darmon1995}[\S 16]{Matsumura1986}
    The Koszul complex associated to a sequence \(\underline{x} = (x_1, \dots, x_n)\) contained in the maximal ideal
    of a local ring is given by the complex
    \[
        0 \to K_n(\underline{x}, R) \xrightarrow{d_n} K_{n-1}(\underline{x}, R) \to \dots \to K_{0}(\underline{x},R) \to 0,
    \]
    where 
    \[
        K_p(\underline{x}, R) \coloneqq \bigoplus_{i_1 < \dots < i_p} R \cdot u_{i_1}\wedge\dots\wedge u_{i_p}
    \]
    for symbols \(u_1, \dots, u_n\). The differential map \(d_p\colon K_p(\underline{x}, R) \to K_{p-1}(\underline{x}, R)\)
    is given by
    \[
        d_p(u_{i_1}\wedge\dots\wedge u_{i_p}) = \sum_{t=1}^p(-1)^t x_{i_t} \cdot 
        u_{i_1} \wedge \dots \wedge \widehat{u_{i_t}}\wedge \dots \wedge u_{i_p}.
    \]
    We denote the \(p\)-th homology group of this complex as \(H_p(\underline{x}, R)\).
\end{definition}

\begin{remark}\textup{\cites[proposition 5.13]{Darmon1995}[theorem 16.5 (i)]{Matsumura1986}}\label{rem:koszul}
    We note that \(K_0(\underline{x}, R) = R\) and therefore compute
    \[
        H_0(\underline{x}, R) = K_0(\underline{x}, R)/(\im d_1) \cong R/(x_1, \dots, x_n) = R/(\underline{x}).
    \]
    Furthermore, one can show that if \((\underline{x})\) is a regular sequence, then the complex is exact.
    As it consists of free \(R\)-modules, homological algebra shows that we then get a resolution of
    \(H_0(\underline{x}, R) = R/(\underline{x})\) by free \(R\)-modules. 
    %if I have time and motivation I can probably give some more proofs here
\end{remark}

\subsection{Complete intersections and Gorenstein rings}
The goal of this section is to show that finite flat complete intersections
satisfy a Gorenstein condition, i.e. a specific form of self-duality.
This fact can then be used to show (c) \(\implies\) (b) in \cref{thm:wiles_numerical_criterion}.
Although there is a very general notion of Gorenstein rings, for
the purpose of this proof we only need a special case,
\begin{definition}
    Let \(A \in \co\) be finite flat. \(A\) is called Gorenstein, if there is an isomorphism of \(A\)-modules
    \[
        \Psi\colon \hom_\mathcal{O}(A, \mathcal{O}) \cong A.
    \]
\end{definition}
Let from now on in this subsection \(A\) be a finite flat complete intersection in \(\cob\). 
Fix a presentation \(A = \mathcal{O}[[X_1,\dots,X_n]]/(f_1,\dots,f_n)\) for a suitable \(n\)
and suitable \(f_i\).
Our goal is to find an \(A\)-module isomorphism
\[
    \hom_\mathcal{O}(A, \mathcal{O}) \to A.
\]
We start with some useful constructions and conventions.
\begin{notation}
    For any ring \(R\) write \(R[[\underline{X}]] \coloneqq R[[X_1, \dots, X_n]]\).
\end{notation}
Let \(a_1, \dots, a_n\) be the images in \(A\) of \(X_1, \dots, X_n\) by the natural map
\[
    \alpha \colon \mathcal{O}[[\underline{X}]] \to A = \mathcal{O}[[\underline{X}]]/(f_1, \dots, f_n),
\]
and let
\[
    \beta \colon A[[\underline{X}]] \to A  
\]
be the map which sends \(X_i\) to \(a_i\). 
A polynomial \(f \in A[[\underline{X}]]\) is sent to \(0\) exactly when \(f(a_1, \dots, a_n) = 0\).
Therefore, \(\exists i\colon\; (X_i - a_i)|f\) and hence, 
the sequence \(g_i =  (X_i - a_i)\) generates the kernel of \(\beta\).
View the \(f_i\) as polynomials in \(A[[\underline{X}]]\) via the inclusion \(O \hookrightarrow A\). 
Then \(\forall i = 1, \dots, n\colon\)
\[
    \beta(f_i) = f_i(a_1, \dots, a_n) = 0 \in \mathcal{O}[[\underline{X}]]/(f_1, \dots, f_n).
\]
Therefore every of the \(f_i\) is element of \(\ker \beta\) and hence can be written as 
an \(A[[X]]\)-linear combination of the \(g_i\),
\[
    (f_1, \dots, f_n) = (g_1, \dots, g_n)M,  
\]
where \(M\) is an \(n \times n\) matrix with coefficients in \(A[[\underline{X}]]\). 
Let \(D = \det(M) \in A[[\underline{X}]]\).
The projection \(\mathcal{O}[[\underline{X}]] \to A\) induces an \(\mathcal{O}[[\underline{X}]]\)-module 
structure on \(A\).

\begin{lemma}\textup{\cite[see][lemma 5.14]{Darmon1995}}\label{lem:surjectivity}
    The map
    \begin{align*}
        \Phi\colon \hom_{\mathcal{O}[[\underline{X}]]}(A[[\underline{X}]], \mathcal{O}[[\underline{x}]]) &\to A\\
        f &\mapsto \alpha(f(D))
    \end{align*}
    is an \(\mathcal{O}[[\underline{X}]]\)-linear surjection.
\end{lemma}
\begin{proof}
    As shown in \cref{lem:reg_seq}, \((\underline{f}) = (f_1, \dots, f_n)\) 
    is a regular sequence for \(\mathcal{O}[[\underline{X}]]\).
    In the ring \(A[[\underline{X}]]/(X_1 - a_1, \dots, X_{i-1} - a_{i-1})\), there are no relations in \(X_i\),
    i.e. it can be written as \(R[X_i]\) for a ring \(R\). Therefore \((X_i - a_i)\) can't be a zero-divisor.
    As this holds for all \(i = 1, \dots, n\), \((\underline{g}) = (g_i) = (X_i - a_i)\) is a regular sequence 
    for \(A[[\underline{X}]]\).
    
    Let now \(K(\underline{f}, \mathcal{O}[[\underline{X}]])\) and \(K(\underline{g}, A[[\underline{X}]])\)
    be the associated Koszul complexes. 
    %Koszul complex property 1:
    By \cref{rem:koszul}, we deduce that \(K(\underline{f}, \mathcal{O}[[\underline{X}]])\) is a resolution of 
    \[
        A = H_0(\underline{f}, \mathcal{O}[[\underline{X}]]) = \mathcal{O}[[\underline{X}]]/(f_1, \dots, f_n)
    \]
    by free \(\mathcal{O}[[\underline{X}]]\)-modules
    and analogous that \(K(\underline{g}, A[[\underline{X}]])\) is a resolution of
    \[
        A = H_0(\underline{g}, A[[\underline{X}]]) = A[[\underline{X}]]/(X_1 - a_1, \dots, X_n-a_n)
    \]
    by free \(A[[\underline{X}]]\)-modules.
    Every free \(A[[\underline{X}]]\)-module has a canonical \(\mathcal{O}[[\underline{X}]]\)-module structure 
    and is free over \(\mathcal{O}[[\underline{X}]]\)
    (take the canonical inclusion \(\mathcal{O} \hookrightarrow A,\; x \mapsto x\cdot 1\) and extend it to a map
    \(\mathcal{O}[[\underline{X}]] \hookrightarrow A[[\underline{X}]]\)).

    In the following, we want to construct a map of complexes
    \[\Phi\colon K(\underline{f}, \mathcal{O}[[\underline{X}]]) \to K(\underline{g}, A[[\underline{X}]]).\]
    On level 0, we define 
    \[
        \phi_0 \colon K_0(\underline{f}, \mathcal{O}[[\underline{X}]]) = \mathcal{O}[[\underline{X}]] 
        \to 
        K_0(\underline{g}, A[[\underline{X}]]) = A[[\underline{X}]]
    \]
    to be just the canonical inclusion \(\mathcal{O}[[\underline{X}]] \hookrightarrow A[[\underline{X}]]\)
    as explained above.
    %Koszul complex property 2:
    On the first level, let
    \[
        \Phi_1 \colon 
            K_1(\underline{f}, \mathcal{O}[[\underline{X}]]) = \bigoplus_{i = 1}^n R \cdot u_i
            \to 
            K_1(\underline{g}, A[[\underline{X}]]) = \bigoplus_{i=1}^n R \cdot v_i
    \]
    be the map defined by
    \[
        (\Phi_1(u_1), \dots, \Phi_1(u_n)) = (v_1, \dots, v_n)M. %probably explain this in greater detail
    \]
    By skew-linearity this can be extended to a map of exterior algebras. %What exactly is an exterior algebra?
    In the following we show that \(\Phi\)
    \begin{enumerate}
        \item is a morphism of complexes,
        \item induces the identity on \(A = H_0(\underline{f}, \mathcal{O}[[\underline{X}]])\)
        \item and satisfies
        \[
            \Phi_n(u_1 \wedge \dots \wedge u_n) = D \cdot v_1 \wedge \dots \wedge v_n.  
        \]
    \end{enumerate}
    \begin{enumerate}
        \item \textbf{\(\Phi\) is a morphism of complexes.}
        It is clear by definition that \(\Phi\) is welldefined on every level.
        We have to show that \(\Phi\) commutes with the differentials of the complex,
        \begin{align*}
            \Phi_{p-1}(d(u_{i_1}\!\wedge\!\dots\!\wedge\!u_{i_p})) 
            &= \Phi_{p-1}\left(\sum_{t=1}^p(-1)^t x_{i_t} 
            u_{i_1}\!\wedge\!\dots\!\wedge\!\widehat{u_{i_t}}\!\wedge\!\dots\!\wedge\!u_{i_p}\right)\\
            &= \sum_{t=1}^p(-1)^t x_{i_t}\Phi_1(u_{i_1})\!\wedge\!\dots\!
            \wedge\widehat{\Phi_1(u_{i_t})}\!\wedge\!\dots\!\wedge\!\Phi_1(u_{i_p})\\
            &= d(\Phi_1(u_{i_1})\wedge\dots\wedge \Phi_1(u_{i_p}))\\
            &= d(\Phi_p(u_{i_1}\wedge\dots\wedge u_{i_p})).
        \end{align*}
        \item \textbf{\(\Phi\) induces the identity on \(A = H_0(\underline{f}, \mathcal{O}[[\underline{X}]])\)}\\
        We have the following commutative diagram
        \[
            \begin{tikzcd}
                \bigoplus_{i=1}^n u_i \mathcal{O}[[\underline{X}]] = K_1(\underline{f}, \mathcal{O}[[\underline{X}]]) 
                \arrow[r, "d_1"] \arrow[d, "\Phi_1"] & K_0(\underline{f}, \mathcal{O}[[\underline{X}]]) \arrow[r, "d_0"] 
                \arrow[d, hook, "\Phi_0"] = \mathcal{O}[[\underline{X}]] & 0\\
                \bigoplus_{i=1}^n v_i A[[\underline{X}]] = K_1(\underline{g}, A[[\underline{X}]]) 
                \arrow[r, "d_1"] & K_0(\underline{g}, A[[\underline{X}]]) = A[[\underline{X}]] \arrow[r, "d_0"] & 0
            \end{tikzcd}.
        \]
        As 
        \[
            H_0(\underline{f}, \mathcal{O}[[\underline{X}]]) = \frac{\ker d_0}{\im d_1} 
            = \frac{\mathcal{O}[[\underline{X}]]}{(f_1, \dots, f_n)}
        \] and
        \[
            H_0(\underline{g}, A[[\underline{X}]]) = \frac{\ker d_0}{\im d_1} 
            = \frac{A[[\underline{X}]]}{(g_1, \dots, g_n)}
        \]
        we can take a look at the map
        \[
            \mathcal{O}[[\underline{X}]] \to \frac{A[[\underline{X}]]}{(X_1 - a_1, \dots, X_n - a_n)} = A.
        \]
        This map sends \(X_i\) to \(a_i \in A\).
        By definition of \(A = \mathcal{O}[[\underline{X}]]/(f_1, \dots, f_n)\) and \(a_i\) as image of \(X_i\)
        under \(\alpha\) this is exactly the map \(\alpha\). Hence, the induced map
        \[
            A = \mathcal{O}[[\underline{X}]]/(f_1, \dots, f_n) \to 
            \frac{A[[\underline{X}]]}{(X_1 - a_1, \dots, X_n - a_n)} = A
        \]
        is identity.
        \item Let \(M = (M_{i,j})_{i,j}\). Then we have
        \begin{align*}
            \Phi_n(u_1 \wedge \dots \wedge u_n) &= \Phi(u_1) \wedge \dots \wedge \Phi(u_n)\\
            &= \sum_{j=1}^n v_jM_{j,1} \wedge \dots \wedge \sum_{j=1}^n v_jM_{j,n}\\
            &= \underbrace{\sum_{\sigma \in \mathfrak{S}(n)} (-1)^{\operatorname{sgn}(\sigma)} 
            \prod_{i=1}^n M_{i,\sigma(i)}}_{= \det M} \cdot v_1 \wedge \dots \wedge v_n\\
            &= D \cdot v_1 \wedge \dots \wedge v_n,
        \end{align*}
        where \(\mathfrak{S}(n)\) may denote the group of permutations.
    \end{enumerate}
    In the following we write 
    \(K_\bullet(\underline{f}) = K_\bullet(\underline{f}, \mathcal{O}[[\underline{X}]])\)
    and 
    \(K_\bullet(\underline{g}) = K_\bullet(\underline{g}, A[[\underline{X}]])\).
    By applying the functor \(\hom_{\mathcal{O}[[\underline{X}]]}(-, \mathcal{O}[[\underline{X}]])\)
    to the two free resolutions, we get the following commutative diagram
    \[
        \begin{tikzcd}[column sep=2.2em]
            \arrow[r, "d_{n-1}^*"] & 
            \hom_{\mathcal{O}[[\underline{X}]]}(K_{n-1}(\underline{f}), \mathcal{O}[[\underline{X}]]) 
            \arrow[r, "d_n^*"] &
            \hom_{\mathcal{O}[[\underline{X}]]}(K_n(\underline{f}), \mathcal{O}[[\underline{X}]]) 
            \arrow[r] & 0\\
            \arrow[r, "d_{n-1}^*"] & 
            \hom_{\mathcal{O}[[\underline{X}]]}(K_{n-1}(\underline{g}), \mathcal{O}[[\underline{X}]])
            \arrow[r, "d_n^*"] \arrow[u, "\Phi_{n-1}^*"] &
            \hom_{\mathcal{O}[[\underline{X}]]}(K_n(\underline{g}), \mathcal{O}[[\underline{X}]]) 
            \arrow[r] \arrow[u, "\Phi_{n}^*"] & 0
        \end{tikzcd}.
    \]
    As both resolutions are free and, a fortiori, projective we can use the fact from homological algebra
    that there exists a homotopy equivalence that induces identity on the zero-th homology groups.
    We just follow the construction in the proof and therefore obtain a homotopy equivalence.
    Consider the following commutative diagram with exact rows
    \[
            \begin{tikzcd}
                \bigoplus_{i=1}^n u_i \mathcal{O}[[\underline{X}]] \arrow[r, "d_1"] \arrow[d, dashed] 
                &\mathcal{O}[[\underline{X}]]  \arrow[r, "\alpha"] \arrow[d, dashed] & A \arrow[r] \arrow[d, "\mathrm{id}"] & 0\\
                \bigoplus_{i=1}^n v_i A[[\underline{X}]] \arrow[r, "d_1"] 
                & A[[\underline{X}]] \arrow[r, "X_i \mapsto a_i"] & A \arrow[r] & 0
            \end{tikzcd}.
        \]
    From projectiveness we can conclude that there is a lift of the map \(\mathrm{id} \circ \alpha\) to a map 
    \(\mathcal{O}[[\underline{X}]] \to A[[\underline{X}]]\) along the map \(X_i \mapsto a_i\). 
    As both maps send \(X_i \mapsto a_i\), our lift is given by \(X_i \mapsto X_i\), i.e. it is exactly \(\Phi_0\).
    By commutativity, \((f_1, \dots, f_n) = \im d_1 = \ker \alpha\) maps to the kernel of \(X_i \mapsto a_i\). Therefore, we can lift the map
    \(\Phi_0 \circ d_1\) along the surjective map 
    \[
        d_1 \colon \bigoplus_{i=1}^n v_i A[[\underline{X}]] \to \im d_1 = \ker(X_i \mapsto a_i) = (g_1, \dots, g_n).
    \]
    Using \((f_1, \dots, f_n) = (g_1, \dots, g_n)M\), we obtain for the induced map \(f\)
    \begin{multline*}
        d_1(f(u_i)) = \Phi_0(d_1(u_i)) = \Phi_0(-f_i)\\ = - \sum_{j=1}^n g_jm_{ji}
        = \sum_{j=1}^n d_1(v_j)m_{ji} = d_1\left(\sum_{j=1}^n v_j m_{ji}\right).
    \end{multline*}
    Choosing \(f = \Phi_1\) satisfies the above equation.
    As the higher maps are then uniquely defined by skew linearity,  \(\Phi\) extends to a homotopy equivalence.
    As \(\hom_{\mathcal{O}[[\underline{X}]]}(-, \mathcal{O}[[\underline{X}]])\) is an additive functor, 
    \(\Phi^*\) is also a homotopy equivalence. Hence,we have an isomorphism on the \(n\)-th cohomology,
    \[
        \Phi_n^*\colon \hom_{\mathcal{O}[[\underline{X}]]}(K_n(\underline{g}), \mathcal{O}[[\underline{X}]])/(\im d_n^*)
        \to \hom_{\mathcal{O}[[\underline{X}]]}(K_n(\underline{f}), \mathcal{O}[[\underline{X}]])/(\im d_n^*).
    \]
    We know that 
    \begin{alignat*}{3}
        &K_n(\underline{f}) &&= \bigoplus_{i = 1}^n \mathcal{O}[[\underline{X}]] \cdot u_1\wedge\dots\wedge u_n
        &&\cong \mathcal{O}[[\underline{X}]]\qquad\text{ and}\\
        &K_n(\underline{g}) &&= \bigoplus_{i = 1}^n A[[\underline{X}]] \cdot u_1\wedge\dots\wedge u_n 
        &&\cong A[[\underline{X}]]. 
    \end{alignat*}
    Therefore, we can make the identification
    \[
        \hom_{\mathcal{O}[[\underline{X}]]}(K_n(\underline{f}), \mathcal{O}[[\underline{X}]])
        \cong \hom_{\mathcal{O}[[\underline{X}]]}(\mathcal{O}[[\underline{X}]], \mathcal{O}[[\underline{X}]])
        \cong \mathcal{O}[[\underline{X}]],
    \]
    where the second isomorphism sends \(f \mapsto f(1)\). The lift of \(1\) under the first isomorphism is 
    \(u_1\wedge\dots\wedge u_n\). Hence in total we send a map 
    \(f\) to \(f(u_1\wedge\dots\wedge u_n)\).
    As a next step, we compute the image of \(d_n^*\) in \(\mathcal{O}[[\underline{X}]]\).
    Let \(\varphi \in \hom_{\mathcal{O}[[\underline{X}]]}(K_{n-1}(\underline{f}), \mathcal{O}[[\underline{X}]])\).
    Then we have
    \[
        d_n^*(\varphi) = \varphi \circ d_n \colon K_n(\underline{f}) \xrightarrow{d_n} K_{n-1}(g) \xrightarrow{\varphi} 
        \mathcal{O}[[\underline{X}]],  
    \]
    where the composition is given by 
    \[
        \varphi(d_n(u_1 \wedge \dots \wedge u_n)) = \sum_{t=1}^n (-1)^t f_t 
        \varphi(v_1 \wedge \dots \wedge \widehat{v_t} \wedge \dots \wedge v_n), 
    \]
    as \(\varphi\) is \(\mathcal{O}[[\underline{X}]]\)-linear.
    By our identification we then send the whole map to 
    \[
        \varphi \circ d_n(u_1\wedge\dots\wedge u_n) = \sum_{t=1}^n (-1)^t f_t 
        \varphi(v_1 \wedge \dots \wedge \widehat{v_t} \wedge \dots \wedge v_n) \in \mathcal{O}[[\underline{X}]].
    \]
    The image of \(d_n^*\) is therefore generated by the \(f_t\) and we get 
    \[
        \hom_{\mathcal{O}[[\underline{X}]]}(K_n(\underline{f}), \mathcal{O}[[\underline{X}]])/(\im d_n^*) 
        \cong \mathcal{O}[[\underline{X}]]/(f_1, \dots, f_n) = A.
    \]
    As a result, \(\Phi_n^*\) induces a \(\mathcal{O}[[\underline{X}]]\)-linear surjection
    \[
        \Phi\colon \hom_{\mathcal{O}[[\underline{X}]]}(A[[\underline{X}]], \mathcal{O}[[\underline{X}]]) \cong 
        \hom_{\mathcal{O}[[\underline{X}]]}(K_n(\underline{g}), \mathcal{O}[[\underline{X}]]) \twoheadrightarrow A.
    \]
    \(\Phi\) takes a \(\mathcal{O}[[\underline{X}]]\)-linear map and applies \(\Phi_n^*\) to \(f\), resulting in 
    \[
        f \circ \Phi_n\colon \mathcal{O}[[\underline{X}]] \xrightarrow{\Phi_n} K_n(g) 
        \xrightarrow{f} \mathcal{O}[[\underline{X}]].
    \]
    After that it uses our previous identification 
    \(\hom_{\mathcal{O}[[\underline{X}]]}(\mathcal{O}[[\underline{X}]], \mathcal{O}[[\underline{X}]])
    \cong \mathcal{O}[[\underline{X}]]\) 
    and sends \(f \circ \Phi_n\) to its value on \(1\). Using the identifications 
    \(K_n(\underline{f})\cong \mathcal{O}[[\underline{X}]]\) and \(K_n(\underline{g})\cong A[[\underline{X}]]\), we obtain
    \[
        f \circ \Phi_n(1) = f \circ \Phi_n(u_1\wedge\dots\wedge u_n) = f(D\cdot v_1\wedge\dots\wedge v_n) = f(D).
    \]
    Finally we have to take the residue class \(\!\!\!\mod (f_1, \dots, f_n)\). 
    That is done by applying the projection map \(\alpha\). In total we get
    \[
        \Phi(f) = \alpha(f(D)),  
    \]
    as desired.
\end{proof}

\begin{lemma}\textup{\cite[lemma 5.15]{Darmon1995}}\label{lem:gorenstein}
    Let 
    \[
        \!\tilde{\cdot}\colon \hom_\mathcal{O}(A, \mathcal{O}) \to 
        \hom_{\mathcal{O}[[\underline{X}]]}(A[[\underline{X}]], \mathcal{O}[[\underline{X}]])
    \]
    be the map that assigns an \(\mathcal{O}[[\underline{X}]]\)-homomorphism
    \(\tilde f\colon A[[\underline{X}]] \to \mathcal{O}[[\underline{X}]]\) to the \(\mathcal{O}\)-homomorphism
    \(f \colon A \to \mathcal{O}\) by extending it with \(X \mapsto X\).
    Then define
    \[
        \Psi \colon \hom_\mathcal{O}(A, \mathcal{O}) \to A  
    \]
    via \(\Psi(f) = \alpha(\tilde{f}(D))\).
    This is an \(A\)-module isomorphism where the \(A\)-module structure on \(\hom_\mathcal{O}(A, \mathcal{O})\)
    is given by \(a \cdot f = (x \mapsto f(ax))\).
    In particular, \(A\) is Gorenstein.
\end{lemma}
\begin{proof}
    \begin{enumerate}
        \item \(\Psi\) is \(A\)-linear. This is the key point of this proof.
        For any \(a \in A, a' \in \mathcal{O}[[\underline{X}]]\) we have by definition of \(\Psi\)
        \[
            \Psi(af) = \alpha(\tilde f(aD)) = \alpha(\tilde f((a - a')D + a'D))
            = \alpha(\tilde f((a-a')D)) + \alpha(\tilde f(a'D)),
        \]
        where in the last step we have used the linearity of \(\tilde f\) and \(\alpha\).
        Now choose \(a' \in \alpha^{-1}(a) \subset \mathcal{O}[[\underline{X}]]\), as \(\alpha\) is surjective.
        We can also understand \(a'\) as an element of \(A[[\underline{X}]]\) via the inclusion
        \(\iota\colon\mathcal{O}[[\underline{X}]] \hookrightarrow A[[\underline{X}]]\).
        It follows \(\beta(\iota(a')) = \alpha(a') = a = \beta(a)\). Therefore, \(a - \iota(a') \in \ker \beta\).
        By definition of the \(g_i\) as generators of \(\ker \beta\), we can write \(a - \iota(a')\) as an 
        \(A[[\underline{X}]]\)-linear combination of the \(g_i\).
        We further have
        \[
            (f_1, \dots, f_n) = (g_1, \dots, g_n) \cdot M.
        \]
        Multiplying with the adjugate matrix \(M'\) we get
        \[  
            (f_1, \dots, f_n) \cdot M' = (g_1, \dots, g_n) \cdot \underbrace{M \cdot M'}_{= D \cdot I_{n\times n}}.
        \]
        Hence, we can write \(g_i \cdot D\) (and therefore also \((a - \iota(a'))\cdot D\)) 
        as an \(A[[\underline{X}]]\)-linear combination of the \(f_i\),
        \[
            (a - \iota(a'))\cdot D = \sum_{i=1}^n a_i f_i.
        \]
        Using the \(\mathcal{O}[[\underline{X}]]\)-linearity of \(\tilde f\), we compute
        \begin{multline*}
            \alpha(\tilde f((a-a')D)) = \alpha\left(\tilde{f}\left(\sum_{i=1}^n a_i f_i\right)\right)\\
            = \alpha\left(\sum_{i=1}^n f_i \tilde{f}(a_i)\right) = \sum_{i=1}^n \alpha(f_i \cdot \tilde{f}(a_i)) = 0,
        \end{multline*}
        as \(f_i \in \ker \alpha\).
        Putting our results together, we obtain
        \[
            \Psi(af) = \alpha(\tilde f((a-a')D)) + \alpha(\tilde f(a'D)) = \alpha(\tilde f(a'D)),
        \]
        and again by \(\mathcal{O}[[\underline{X}]]\)-linearity of \(\tilde f\) we conclude
        \[
            \Psi(af) = \alpha(a'\tilde f(D)) = a \alpha(\tilde f(D)) = a \Psi(f).
        \]
        \item \(\Psi\) is surjective.
        As \(A\) is a finite flat \(O\)-algebra, we know by the classification of finitely generated modules
        over principal ideal domains that \(A\) consists of a free part and a torsion part. Because it is flat,
        however, the torsion part is 0 and therefore \(A\) is a free \(O\)-module.
        Therefore we have \(\mathcal{O}\)-module-isomorphisms
        \[
            \hom_\mathcal{O}(A, \mathcal{O}) \cong \hom_\mathcal{O}(\mathcal{O}^r, \mathcal{O})
            \cong \mathcal{O}^r,
        \]
        where \(r\) may denote the rank of \(\mathcal{O}\). 
        Therefore \(A\) and \(\hom_\mathcal{O}(A, \mathcal{O})\) are both free \(A\)-modules of the 
        same finite rank \(r\). Now let us consider base change from \(\mathcal{O}\) to \(\mathcal{O}[[\underline{X}]]\).
        We have an \(\mathcal{O}[[\underline{X}]]\)-module isomorphism \cite[cf.][\href{https://stacks.math.columbia.edu/tag/05G3}{tag 05G3}]{stacks-project}
        \[
            \hom_\mathcal{O}(A, \mathcal{O}[[\underline{X}]])
            \cong \hom_{\mathcal{O}[[\underline{X}]]}(A[[\underline{X}]], \mathcal{O}[[\underline{X}]]).
        \]
        Furthermore, as \(\mathcal{O}[[\underline{X}]]\) is flat and \(A\) is finitely presented as \(\mathcal{O}\)-modules, 
        we obtain
        \[
            \hom_\mathcal{O}(A, \mathcal{O}[[\underline{X}]]) 
            \cong \hom_\mathcal{O}(A, \mathcal{O}) \otimes_\mathcal{O}\mathcal{O}[[\underline{X}]]
        \]
        \cite[chapter I, \S 2, section 9]{Bourbaki1989}.
        Therefore, an \(\mathcal{O}\)-basis \(f_1, \dots, f_r\) of \(\hom_\mathcal{O}(A, \mathcal{O})\) is 
        an \(\mathcal{O}[[\underline{X}]]\)-basis of \(\hom_\mathcal{O}(A, \mathcal{O}[[\underline{X}]])\) and
        by base change, the extended maps \(\tilde f_1, \dots \tilde f_r\) form an \(\mathcal{O}[[\underline{X}]]\)-basis
        of 
        \[ 
            \hom_{\mathcal{O}[[X]]}(A[[\underline{X}]], \mathcal{O}[[\underline{X}]]).
        \]
        \Cref{lem:surjectivity} tells us that the map 
        \[
            \Phi\colon \hom_{\mathcal{O}[[\underline{X}]]}(A[[\underline{X}]], \mathcal{O}[[\underline{X}]]) \to A
        \]
        is surjective.
        Therefore, \(\forall a \in A\colon \exists p_1, \dots, p_r \in \mathcal{O}[[X]]\) s.t.
        \[
            a = \Phi(p_1 \tilde f_1 + \dots + p_r \tilde f_r).
        \]
        Using that \(\alpha\) is a ring homomorphism in the first linebreak and
        the \(\mathcal{O}\)-linearity of \(\Psi\) in the second, we conclude
        \begin{align*} 
                a &= \alpha((p_1 \tilde f_1 + \dots + p_r \tilde f_r)(D))\\
                &= \sum_{i=1}^r \alpha(p_i)\cdot \alpha(\tilde{f}_i)(D) = \sum_{i=1}^r \alpha(p_i) \cdot \Psi(f_i)\\
                &= \Psi(\alpha(p_1) f_1 + \dots + \alpha(p_r) f_r).
        \end{align*}
        \item \(\Psi\) is injective.
        Analogous to the theorem for vector spaces, we know that a surjective homomorphism between two free modules 
        of the same finite rank is also injective.
        (Note that the reverse implication doesn't hold, injective homomorphisms between free modules of the same
        finite rank are not necessarily surjective.)
        As this condition is satisfied by \(\hom_\mathcal{O}(A, \mathcal{O})\) and \(A\), 
        the lemma follows.
    \end{enumerate}
\end{proof}

\subsection{Explicit computation of \texorpdfstring{\(\eta\)}{} for complete intersections}

In this section, \(A\) is always a finite flat complete intersection in \(\cob\), 
i.e. we can fix a presentation \(A \cong \mathcal{O}[[X_1, \dots, X_n]]/(f_1, \dots, f_n)\).
The goal of this section is to find explicit formulas for \(\eta_A\) and \(\phi_A\) using
the relations \(f_i\). This allows us to show that (c) \(\implies\) (b) in \cref{thm:wiles_numerical_criterion}.
We closely follow \cite[chapter 5.4]{Darmon1995}.
\begin{notation}
    \(A^\vee \coloneqq \hom_\mathcal{O}(A, \mathcal{O})\) and similarly, \(\pi_A^\vee \colon \mathcal{O}^\vee \to A^\vee\) 
    may denote the dual map associated to \(\pi_A\colon A \to \mathcal{O}\).
\end{notation}
As \(A\) is a complete intersection, \cref{lem:gorenstein} tells us that \(A^\vee \cong A\).
We choose one \(A\)-module isomorphism \(\Psi\colon A^\vee \to A\).
\begin{lemma}
    Any two \(A\)-module isomorphisms \(\Psi, \Psi' \colon A^\vee \to A\) differ by a unit in \(A\).
\end{lemma}
\begin{proof}
    The composition \(\Psi' \circ \Psi^{-1} \colon A \to A\) is an \(A\)-module isomorphism from \(A\) to \(A\).
    Such an isomorphism is uniquely defined by its value on \(1\),
    \[
        \Psi' \circ \Psi^{-1}(x) = x \cdot \Psi' \circ \Psi^{-1}(1).
    \]
    Analogously, the inverse map is also just multiplication with some element of \(A\).
    Multiplication with these two elements then is identity, so they are inverse and
    \(\Psi' \circ \Psi^{-1}(1) \in A^\times\).
    \(\Psi \circ \Psi^{-1}(1) = 1\), so \(\Psi' \circ \Psi^{-1} = x \cdot \Psi \circ \Psi^{-1}\).
    We conclude \(\Psi = x \cdot \Psi'\).
\end{proof}

\begin{lemma}
    Regardless of the choice of \(\Psi,\) we have 
    \(\Psi \pi_A^\vee(\mathcal{O}^\vee) = \ann_A \ker \pi_A\) and, a fortiori
    \[
        \eta_A = \pi_A \Psi \pi_A^\vee(\mathcal{O}^\vee).  
    \]
\end{lemma}
\begin{proof}
    We first show \(\Psi \pi_A^\vee(\mathcal{O}^\vee) \subset \ann_A \ker \pi_A\).
    Let therefore \(\phi\colon \mathcal{O} \to \mathcal{O} \in \mathcal{O}^\vee\) and \(x \in \ker \pi_A\).
    It suffices to show that \(\Psi \pi_A^\vee(\phi) \cdot x = 0\).
    Taking into account the \(A\)-module structure of \(\hom_\mathcal{O}(A, \mathcal{O})\) 
    and the fact that \(\Psi\) is an \(A\)-module-isomorphism, we obtain
    \[
        \Psi \pi_A^\vee(\phi) \cdot x = \Psi(\phi \circ \pi_A) \cdot x = \Psi(x \cdot \phi \circ \pi_A) 
        = \Psi((y \mapsto \phi \circ \pi_A(x\cdot y))) = 0,
    \]
    as \(x \in \ker \pi_A\).
    In order to prove  \(\Psi \pi_A^\vee(\mathcal{O}^\vee) \supset \ann_A \ker \pi_A\), let \(a \in \ann_A \ker \pi_A\)
    and \(f \in \hom_\mathcal{O}(A, \mathcal{O})\) s.t. \(\Psi(f) = a\). Then \(\forall x \in \ker \pi_A\),
    \[
        0 = \Psi(f) \cdot x = \Psi((y \mapsto f(x\cdot y))) \implies f(x\cdot y) = 0\quad \forall y \in A \implies f(x) = 0.
    \]
    A fortiori, \(\ker \pi_A \subset \ker f\) and we get an induced map \(\tilde f\colon \mathcal{O} \cong A/\ker \pi_A \to \mathcal{O}\)
    s.t. \(f = \tilde f \circ \pi_A\). As a result, we can write
    \[
        a = \Psi(f) = \Psi(\tilde f \circ \pi_A) = \Psi(\pi_A^\vee(\tilde f)) \in \Psi(\pi_A^\vee(\mathcal{O}^\vee)).  
    \]
\end{proof}

\begin{lemma}
    Let 
    \[
        \!\tilde{\cdot}\colon \hom_\mathcal{O}(A, \mathcal{O}) \to 
        \hom_{\mathcal{O}[[\underline{X}]]}(A[[\underline{X}]], \mathcal{O}[[\underline{X}]])
    \]
    and \(\Psi\)
    be the maps known from \cref{lem:gorenstein} and \(D = \det M\) as defined in the previous subsection.
    Then,
    \[
        \pi_A \Psi \pi_A^\vee(\mathcal{O}^\vee) = \langle\pi_A\alpha \tilde \pi_A(D)\rangle_\mathcal{O}.
    \]
\end{lemma}
\begin{proof}
    Let \(\phi \in \mathcal{O}^\vee = \hom_\mathcal{O}(\mathcal{O}, \mathcal{O})\).
    Then \(\phi(x) = x \cdot\phi(1) \in \mathcal{O}\). Therefore 
    \[
        \Psi(\pi_A^\vee(\phi)) = \Psi(\phi \circ \pi_A) = \alpha(\tilde{\phi} \circ \tilde{\pi_A}(D)) = \alpha(\phi(1)\cdot \tilde{\pi_A}(D)).
    \]
    Using the \(\mathcal{O}\)-linearity of \(\alpha\) and \(\pi_A\), we get
    \[
        \pi_A(\Psi(\pi_A^\vee(\phi))) = \phi(1) \cdot \pi_A \alpha \tilde{\pi_A}(D) \in \langle\pi_A\alpha \tilde \pi_A(D)\rangle_\mathcal{O}.
    \]
    For the other inclusion, let \(x\cdot \pi_A\alpha\tilde \pi_A \in \langle\pi_A\alpha \tilde \pi_A(D)\rangle_\mathcal{O}\) 
    with \(x \in \mathcal{O}\). Then define \(\phi(y) = y \cdot x \in \mathcal{O}^\vee\).
    By the calculations we have done so far it becomes clear that this is the required preimage.
\end{proof}

\begin{proposition}\textup{\cite[proposition 5.19]{Darmon1995}}
    \[
        \eta_A = (\det(\partial f_i/\partial X_j(0))).
    \]
\end{proposition}
\begin{proof}
    We have \[
        \eta_A = \pi_A \Psi \pi_A^\vee(\mathcal{O}^\vee) = \langle\pi_A\alpha \tilde \pi_A(D)\rangle_\mathcal{O}.
    \]
    Consider the equation
    \[
        (f_1, \dots, f_n) = (X_1 - [X_1], \dots, X_n - [X_n]) \cdot (m_{i,j})_{i,j}.
    \]
    Applying \(\tilde \pi_A\) to the whole equation leaves the \(f_i\) unchanged because \(\tilde \pi_A(X_i) = X_i\)
    and the coefficients of the \(f_i\) are elements of \(\mathcal{O}\) that are not affected by \(\pi_A\)
    because of its \(\mathcal{O}\)-linearity.
    In the following we make use of \cref{rem:noconstant}.
    On the RHS, we get \(\tilde \pi_A(X_i - [X_i]) = X_i - \pi_A([X_i]) = X_i\), as \(\pi_A\) 
    is the evaluation at \(0\) for preimages of \(A\) in \(\mathcal{O}[[X_1, \dots, X_n]]\).
    Denote the image of \(m_{i,j}\) under \(\tilde \pi_A\) with \(\tilde m_{i,j} \in \mathcal{O}[[X_1, \dots, X_n]]\).
    Now compute
    \[
        \frac{\partial f_i}{\partial X_j}(0) = \frac{\partial \sum_{k=1}^n X_k\tilde m_{k,i}}{\partial X_j}(0) 
        = \tilde m_{j,i}(0) + \sum_{k=1}^n X_k \frac{\partial \tilde m_{k,i}}{\partial X_j}\bigg|_{0} 
        = \tilde m_{j,i}(0).
    \]
    The composition \(\pi_A \circ \alpha\) is given by the evaluation at \(0\).
    Because computing the determinant is a linear operation, we get
    \[
        \pi_A \alpha \tilde \pi_A(D) = \det(\pi_A\alpha \tilde m_{i,j})_{i,j} = \det(\tilde m_{i,j}(0))_{i,j}
        = \det \frac{\partial f_i}{\partial X_j}(0).
    \]
\end{proof}

\begin{corollary}\textup{\cite[corollary 5.20]{Darmon1995}}\label{cor:cimpliesb}
    Remembering that we assumed \(A\) to be a finite flat complete intersection \(\in \cob\), we obtain
    \[
        \# \Phi_A = \# (\mathcal{O}/\eta_A),
    \]
    i.e. (c)\(\implies\)(b) in \cref{thm:wiles_numerical_criterion}.
    %explain how (c) implies (b)
\end{corollary}
\begin{proof}
    From \cref{rem:tangentspace} we know that 
    \[
        \Phi_A \cong \Phi_U/(\overline{f_1}, \dots, \overline{f_n}),  
    \]
    where \(\overline{f}\) denotes the degree one term of a polynomial. More explicitly, we get
    \[
        \Phi_A \cong \mathcal{O} X_1 \oplus \dots \oplus \mathcal{O} X_n/
        (a_{f_1, 1}X_1 + \dots + a_{f_1, n}X_n, \dots, a_{f_n, 1}X_1 + \dots + a_{f_n, n}X_n).  
    \]
    Applying the isomorphism \(\Phi_U = \mathcal{O}^n\) we obtain
    \[
        \Phi_A \cong \mathcal{O}^n/(v_1, \dots, v_n),
    \]
    where \(v_i \coloneqq (a_{f_i, 1}, \dots, a_{f_i, n})\).
    If we interpret \(V = [v_i]_i\) as a matrix and thereby as an \(\mathcal{O}^n\)-endomorphism, 
    we have \(\im V = (v_1, \dots, v_n)\).
    Clearly,
    \[
        a_{f_i, j} = \frac{\partial f_i}{\partial X_j}(0)  
    \]
    and hence,
    \[
        V = \left(\frac{\partial f_i}{\partial X_j}(0)\right)_{i, j}.
    \]
    As \(\mathcal{O}\) is a PID, we know that there exist invertible \(\mathcal{O}\)-matrices \(S,T\) s.t.
    \[
        V = SDT  
    \]
    for some diagonal matrix 
    \[
        D = \begin{pmatrix}
            d_1&&\\
            &\ddots&\\
            &&d_n
        \end{pmatrix}
    \]
    (Smith normal form).
    As the endomorphisms enduced by \(S\) and \(T\) are isomorphisms, we compute
    \[
        \mathcal{O}^n/(SDT)\mathcal{O}^n = \mathcal{O}^n/D\mathcal{O}^n = 
        \mathcal{O}/d_1\mathcal{O} \oplus \dots \oplus \mathcal{O}/d_n\mathcal{O}
    \]
    For Dedekind rings we know that \(A/\mathfrak{a}A \cong \mathfrak{b}/\mathfrak{a}\mathfrak{b}\)
    if \(0\neq \mathfrak{a},\mathfrak{b}\) are ideals of \(A\).
    We conclude
    \[
        \# \mathcal{O}/\mathfrak{a}\mathfrak{b} 
        \cong \#\mathcal{O}/\mathfrak{b} \cdot \# \mathfrak{b}/\mathfrak{a}\mathfrak{b} 
        \cong \#\mathcal{O}/\mathfrak{b} \cdot \#\mathcal{O}/\mathfrak{a}
    \]
    and obtain
    \[
        \# \mathcal{O}^n/D\mathcal{O}^n 
        = \# \mathcal{O}/d_1\mathcal{O} \cdot \dots \cdot \# \mathcal{O}/d_n\mathcal{O}
        = \# \mathcal{O}/(d_1\cdot \dots \cdot d_n)\mathcal{O} = \# \mathcal{O}/(\det D)\mathcal{O}
    \]
    With \(\# \mathcal{O}/(\det D)\mathcal{O} = \# \mathcal{O}/(\det V)\mathcal{O}\)
    and
    \[
        (\det V) \mathcal{O} = \det (\frac{\partial f_i}{\partial X_j}(0)) \mathcal{O} = \eta_A,
    \]
    we conclude
    \[
        \# \Phi_A = \# \mathcal{O}^n/V\mathcal{O}^n =  \# \mathcal{O}/\det V\mathcal{O} = \# \mathcal{O}/\eta_A.
    \]
\end{proof}

\subsection{Isomorphism theorems}

\begin{proposition}\textup{\cite[theorem 5.21]{Darmon1995}}\label{prop:phi_iso}
    Let \(f\colon A \twoheadrightarrow B\) be a \(\cob\)-morphism and \(B\) a finite flat complete intersection.
    If the tangent spaces \(\phi_A, \phi_B\) are finite and 
    the induced morphism \(\tilde f\colon \phi_A \to \phi_B\) is an isomorphism,
    then \(f\) is an isomorphism.
\end{proposition}
\begin{proof}
    Consider the following commutative diagram
    \[
        \begin{tikzcd}
             & A \arrow[dd, "f", two heads] \arrow[rd, "\pi_A", two heads] 
             & \arrow[l, hook]\ker \pi_A \arrow[r, two heads]
             & \phi_A \arrow[dd, hook, two heads, "\tilde f"]\\
            U \arrow[ru, "\nu_A", two heads]\arrow[rd, "\nu_B"', two heads] & & \mathcal{O}&\\
             & B \arrow[ru, "\pi_B"', two heads] & \arrow[l, hook]\ker \pi_B \arrow[r, two heads] & \phi_B.
        \end{tikzcd}
    \]
    The projection \(\nu_B\) arises from the fact that we can write every object in \(\cob\)
    as a quotient of \(U\) (\cref{rem:quotientofU}).
    As \(B\) is a complete intersection, we find \(n\) generators \(f_i \in U\) s.t. \(\ker \nu_B = (f_1, \dots, f_n)\).
    Note that we need to choose the \(f_i\) in such a way that they have no constant term (cf. \cref{rem:noconstant}).
    Define \(b_i \coloneqq \nu_B(X_i) \in \ker \pi_B\) and choose preimages \(a_i \in A\) s.t. \(f(a_i) = b_i\).
    As the triangle involving \(A, B\) and \(\mathcal{O}\) commutes, we conclude that \(\pi_A(a_i) = \pi_B(b_i) = 0\),
    i.e. \(a_i \in \ker \pi_A\).
    
    As \(X_1, \dots, X_n\) generate \(\phi_U\) and \(\nu_B\) is surjective, it follows from \cref{lem:surjectivity_phi}
    that \(b_1, \dots, b_n\) generate \(\phi_B\).
    We know that \(\tilde f\) is an isomorphism, so \(a_1, \dots, a_n\) generate \(\phi_A\).
    Define
    \[
        \nu_A \colon \mathcal{O}[[X_1, \dots, X_n]] \to A
    \] via \(\nu_A(X_i) = a_i\).
    As all generators lie in the image of \(\nu_A\), this induces a surjection on \(\phi_A\).
    By \cref{lem:surjectivity_phi} it follows that \(\nu_A\) is surjective.
    %kernel containments => well defined inverse => \phi is an iso
    
    Finally, we want to show that \(\ker \nu_A = \ker \nu_B\).
    Let \(x \in \ker \nu_A\), i.e. \(0 = f(0) = f(\nu_A(x)) = \nu_B(x)\), i.e. \(x \in \ker \nu_B\).
    Therefore it remains to prove the inclusion \(\ker \nu_B \subset \ker \nu_A\).
    
    The kernel of
    \[
        \overline{\nu_A} \colon \phi_U \to \phi_A  
    \]
    is a submodule of the finitely generated \(\mathcal{O}\)-module \(\phi_U\) that has rank \(n\).
    As \(\mathcal{O}\) is a PID, we know that any submodule is finitely generated of rank \(n' \leq n\).
    Independent of \(n'\), we can choose \(n\) possibly linear dependent generators 
    \(\overline{g_1}, \dots \overline{g_n}\) of the above kernel and then extend these generators to 
    \(g_1, \dots, g_n \in \ker \nu_A\). A fortiori, the \(g_i\) do not have constant terms.

    As the kernel of \(\nu_B\) is generated by \(f_1, \dots, f_n\) and \(\ker \nu_A \subset \ker \nu_B\),
    we find a \(U\)-linear combination that can be written in the form
    \[
        (g_1, \dots, g_n) = (f_1, \dots, f_n) \cdot M,
    \]
    where \(M\) is a \(n \times n\) matrix with entries in \(U\).
    The \(g_i\) and the \(f_i\) both have no constant terms. If we forget all monomials 
    of degree bigger than one (or equivalently consider the residue classes mod \(\ker \pi_A^2\) 
    resp. \(\ker \pi_B^2\), denoted by \(\overline{\cdot}\)), the resulting polynomials
    \(\overline{f_i}, \overline{g_i}\) are sums of monomials of degree 1.
    Therefore, only the constant terms \(M^\mathrm{const}\) of \(M\) influence the \(\overline{g_i}\) and we get
    \[
        (\overline{g_1}, \dots, \overline{g_n}) = (\overline{f_1}, \dots, \overline{f_n})M^\mathrm{const}.
    \]
    As \(\phi_A\) and \(\phi_B\) are isomorphic,
    \[ 
        (\overline{f_1}, \dots, \overline{f_n}) = \ker(\phi_U \xrightarrow{\overline{\nu}_B} \phi_B)
        \cong \ker(\phi_U \xrightarrow{\overline{\nu}_A} \phi_A) = (\overline{g_1}, \dots, \overline{g_n}),
    \]
    i.e. both \((\overline{g_1}, \dots, \overline{g_n})\) and \((\overline{f_1}, \dots, \overline{f_n})\) 
    generate the same \(\mathcal{O}\)-submodule of \(\phi_U\).
    As a result, we can express each of the \(\overline{f_1}, \dots, \overline{f_n}\) as a 
    \(\mathcal{O}\)-linear combination of \((\overline{g_1}, \dots, \overline{g_n})\).
    This gives us an inverse to \(M^\mathrm{const}\) and we deduce that \(\det M^\mathrm{const}\) is invertible
    in \(\mathcal{O}\).
    A power series is invertible if its constant term is invertible, so \(\det M\) is invertible
    as well and we conclude that 
    \[ 
        f_1, \dots, f_n \in \langle g_1, \dots, g_n\rangle_U = \ker \nu_B
    \]
    and, a fortiori, 
    \[
        \ker \nu_A = \langle f_1, \dots, f_n\rangle_U \subset \ker \nu_B.
    \]
    In total we obtain \(\ker \nu_A = \ker \nu_B\) and we define the map 
    \[
        \nu_A\nu_B^{-1}\colon B \to A.  
    \]
    This is welldefined: For a given \(x \in B\) choose \(y, y' \in U\) s.t. 
    \(\nu_B(y) = \nu_B(y') = x\). It follows \(y' - y \in \ker \nu_B\). 
    Then \(\nu_A(y') = \nu_A(y'-y) + \nu_A(y) = 0 + \nu_A(y)\) because \(\ker \nu_A = \ker \nu_B\).
    
    From the commutativity of the above diagram we get that this is an inverse for \(f\) and
    hence, \(f\) is an isomorphism.
\end{proof}

\begin{remark}\cite[remark 5.22, remark 5.23]{Darmon1995}
    Let \(A = \mathcal{O}[[X,Y]]/(X(X-\lambda), Y(Y-\lambda))\) be the ring from \cref{ex:ddt4} and 
    \(B = \mathcal{O}[[X,Y]]/(X(X-\lambda), Y(Y-\lambda), XY)\) be the ring from \cref{ex:ddt2} and 
    \(f\colon A \to B\) the canonical projection. Then \(f\) induces an isomorphism on the tangent spaces,
    but is not an isomorphism. The assumption that \(B\) is a complete intersection is necessary.
    However, let \(A = A[[X]]/(X^3)\), \(B = A[[X]]/(X^2)\) and \(f \colon A \to B\) the canonical projection.
    Then \(\phi_A \cong \mathcal{O} \cong \phi_B\) (cf. \cref{ex:ddt3}), even though \(f\) is not an isomorphism:
    the tangent spaces aren't finite.
\end{remark}

\begin{lemma}\label{lem:pontryagininjectivity}
    Let \(A \in \cob\) be finite flat. Then the canonical map
    \[
        A \to A^{\vee\vee}
    \]
    is injective. As a corollary we have
    \[
        A \neq 0 \implies A^\vee \neq 0.  
    \]
\end{lemma}
\begin{proof}
    As \(\mathcal{O}\) is local, every finitely generated torsion-free \(\mathcal{O}\)-module is free and, 
    a fortiori projective. For projective modules we have the existence of a dual basis, i.e. a set of functions
    \[
        \{f_i \colon i \in I, f_i \in A^\vee = \hom_\mathcal{O}(A, \mathcal{O})\}  
    \]
    together with a set of of elements
    \[
        \{a_i \colon i \in I, a_i \in A\}  
    \]
    satisfying the properties
    \begin{enumerate}
        \item \(\forall a \in A\colon \quad \# \{i\in I\colon f_i(a) \neq 0\} < \infty\) and
        \item \(\forall a \in A\colon \quad a = \sum_{i \in I} f_i(a)\cdot a_i\).
    \end{enumerate}
    The canonical map from \(A\) to \(A^{\vee\vee}\) sends \(a\) to \(\operatorname{eval}_a\).
    Now let \(a\) in the kernel of this canonical map. Then, \(\phi(a) = 0\; \forall \phi \in A^\vee\)
    and, a fortiori, \(f_i(a) = 0\; \forall i \in I\).
    We conclude
    \[
        a = \sum_{i \in I} f_i(a)\cdot a_i = 0
    \]
    and hence, \(A \to A^{\vee\vee}\) is injective. If \(A^\vee = 0\) then obviously any homomorphism from \(A^\vee\)
    is \(0\), a fortiori, \(A^{\vee\vee} = 0\). By the injectivity of \(A \to A^{\vee\vee}\) this yields \(A = 0\)
    and we have proved the second part of the lemma.    
\end{proof}

\begin{lemma}\label{lem:intersectionzero}
    Let \(A \in \cob\) be finite flat. Then
    \[
        \ker \pi_A \cap \ann_A \ker \pi_A = 0.  
    \]
\end{lemma}
\begin{proof}
    Let \(0 \neq x \in \eta_A\) and \(x' \in \ann_A \ker \pi_A\) s.t. \(\pi_A(x') = x\).
    Interpret \(x \cdot 1\) as an element of the \(\mathcal{O}\)-module \(A\). Then,
    \[
        \pi_A(x \cdot 1 - x') = x\cdot \pi_A(1) - \pi_A(x') = x - x = 0 \implies x \cdot 1 - x' \in \ker \pi_A.
    \]
    Take \(a \in \ker \pi_A \cap \ann_A \ker \pi_A\). Then \(ax' = 0\), because \(a\in \ker \pi_A\) 
    and \(x' \in \ann_A \ker \pi_A\). Together we obtain
    \[
        0 = a \cdot (x\cdot 1 - x') = x \cdot a,
    \]
    i.e. \(a\) is \(\mathcal{O}\)-torsion. However, \(A\) is flat and, a fortiori, torsion-free. Hence,
    \(a\) is 0.
\end{proof}

\begin{proposition}\textup{\cite[theorem 5.24]{Darmon1995}}\label{prop:eta_iso}
    Let \(f\colon A \twoheadrightarrow B\) be a \(\cob\)-morphism, \(A\) and \(B\) finite flat and \(A\) a 
    complete intersection. If \(\eta_A = \eta_B \neq 0\), then \(f\) is an isomorphism.
\end{proposition}
\begin{proof}
    By \cref{lem:gorenstein}, \(A\) is Gorenstein, i.e.
    \[
        A^\vee = \hom_\mathcal{O}(A, \mathcal{O}) \cong A \quad \text{as \(A\)-modules,} 
    \]
    where the \(A\)-module structure is given via \(a \cdot \phi = (x \mapsto \phi(a\cdot x))\).
    By \cref{lem:intersectionzero} \(\ker \pi_A \cap \ann_A \ker \pi_A = 0\) and likewise for \(B\).
    The fundamental theorem of homomorphisms gives us a \(\mathcal{O}\)-linear isomorphisms
    \[
        \ann_A \ker \pi_A = \ann_A \ker \pi_A/(\ker \pi_A \cap \ann_A \ker \pi_A) \xrightarrow[\sim]{\pi_A} \eta_A
    \]
    respectively
    \[
        \ann_B \ker \pi_B = \ann_B \ker \pi_B/(\ker \pi_B\cap \ann_B \ker \pi_B) \xrightarrow[\sim]{\pi_B} \eta_B.
    \]
    In total we obtain
    \[
        \ann_A \ker \pi_A \cong \eta_A \xhookrightarrow{f} \eta_B \cong \ann_B \ker \pi_B,
    \]
    where \(f\) is the inclusion by \cref{lem:surjectivity_eta}.
    As \(f\) is a \(\cob\)-map, we have the commutativity \(\pi_A = \pi_Bf\). Hence, for all \(x\in \ker f\)
    we compute \(\pi_A(x) = \pi_B(f(x)) = \pi_B(0) = 0\), i.e. \(x \in \ker \pi_A\). We thereby have shown 
    that \(\ker f \subset \ker \pi_A\) and with \cref{lem:intersectionzero} we conclude
    \[
        \ker f \cap \ann_A \ker \pi_A \subset \ker \pi_A \cap \ann_A \ker \pi_A = 0.
    \]
    A fortiori, we get an exact sequence of \(A\)-modules
    \[
        0 \longrightarrow \ker f \oplus \ann_A \ker \pi_A \longrightarrow A 
        \longrightarrow A/(\ker f \oplus \ann_A \ker \pi_A)  \longrightarrow 0.
        \tag{\textasteriskcentered} \label{eq:ses}
    \]
    We have
    \[
        A/(\ker f \oplus \ann_A \ker \pi_A) \xrightarrow[\sim]{f} B/f(\ann_A \ker \pi_A) \cong B/\ann_B \ker \pi_B
    \]
    and via \([b] \mapsto (x \mapsto b\cdot x)\) we get a canonical injection
    \[
        B/\ann_B \ker \pi_B \hookrightarrow \operatorname{End}_\mathcal{O}(\ker \pi_B).
    \]
    This is a welldefined injection because any element in the annulator of \(\ker \pi_B\) is the zero map
    in \(\operatorname{End}_\mathcal{O}(\ker \pi_B)\) and the zero map always comes from an element in the annulator.
    As \(B\) and therefore \(\ker \pi_B\) are torsion-free, we show that \(\operatorname{End}_\mathcal{O}(\ker \pi_B)\)
    is torsion-free as well. For, let \(0 \neq \phi \in \operatorname{End}_\mathcal{O}(\ker \pi_B)\) and 
    \(x \in \mathcal{O}\) s.t. \(0 = x \cdot \phi = (y \mapsto x \cdot \phi(y))\).
    As \(\phi \neq 0\), there is at least one \(\tilde y \in \ker \pi_B\) s.t. \(\phi(\tilde y) \neq 0\).
    As \(\ker \pi_B\) is torsion-free and \(x \cdot \phi(\tilde y) = 0\) it follows that \(x = 0\), i.e.
    \(\operatorname{End}_\mathcal{O}(\ker \pi_B)\) is torsion-free.
    As \(O\) is a Dedekind ring, torsion-freeness implies flatness. Over any local ring, finite flat
    modules are free and a fortiori projective. Hence, the short exact sequence \eqref{eq:ses} splits.
    Functors preserve split exact sequences and therefore applying the contravariant functor
    \(\hom_\mathcal{O}(-, \mathcal{O})\) yields
    \[
        0 \longrightarrow (A/\ker f \oplus \ann_A \ker \pi_A)^\vee  \longrightarrow A^\vee
        \longrightarrow (\ker f \oplus \ann_A \ker \pi_A)^\vee \longrightarrow 0.
    \]
    The direct sum of modules is a colimit, so it commutes with the 
    \(\hom_\mathcal{O}(-, \mathcal{O})\)-functor and becomes a limit, in this case a product.
    However, a finite product is isomorphic to the finite coproduct in the category of \(\mathcal{O}\)-modules
    and together with the fact that \(A\) is Gorenstein, we obtain
    \[
        A \longrightarrow (\ker f)^\vee \oplus (\ann_A \ker \pi_A)^\vee \longrightarrow 0.
    \]
    The functor \(- \otimes_A k\) (where we interpret \(k\) as an \(A\)-module via the canonical projection
    \(A \xrightarrow{\pi_A} \mathcal{O} \twoheadrightarrow \mathcal{O}/\lambda = k\)) 
    is right exact (because it's left adjoint to the corresponding \(\hom\)-functor).
    Taking the dimension of the resulting exact sequence gives us 
    \[
        1 = \dim_k(A\otimes_A k) \geq \dim_k ((\ker f)^\vee \otimes_A k)
        + \dim_k ((\ann_A \ker \pi_A)^\vee\otimes_A k),
        \tag{\textasteriskcentered\textasteriskcentered} \label{eq:dimineq}
    \]
    because taking the dimension commutes with direct sums.
    It is clear that 
    \[
        \eta_A = \pi_A \ann_A \ker \pi_A \neq 0 \implies \ann_A \ker \pi_A \neq 0.
    \]
    By \cref{lem:pontryagininjectivity}, \((\ann_A\ker \pi_A)^\vee \neq 0\).
    Now let's assume 
    \[
        \dim_k(\ann_A\ker \pi_A)^\vee \otimes_A k = 0.
    \]
    That would imply
    \[
        0 = (\ann_A\ker \pi_A)^\vee \otimes_A A/\lambda = (\ann_A\ker \pi_A)^\vee/\lambda (\ann_A\ker \pi_A)^\vee,
    \]
    which is equivalent to \((\ann_A\ker \pi_A)^\vee = \lambda (\ann_A\ker \pi_A)^\vee\) and
    by Nakayama's lemma for the local ring \(\mathcal{O}\) we could conclude that \((\ann_A\ker \pi_A)^\vee = 0\),
    contradiction. Therefore \(\dim_k (\ann_A\ker \pi_A)^\vee \otimes_A k > 0\) and by \eqref{eq:dimineq} 
    we have \((\ker f)^\vee \otimes_A k = 0\).
    Again,
    \[
        0 = (\ker f)^\vee \otimes_A A/\lambda = (\ker f)^\vee/\lambda(\ker f)^\vee \xRightarrow{Nakayama} (\ker f)^\vee = 0.
    \]
    Taking the dual and applying \cref{lem:pontryagininjectivity} finally yields \(\ker f = 0\).
\end{proof}

\subsection{A resolution lemma}

\begin{lemma}\label{lem:resolution}\textup{\cite[theorem 5.26]{Darmon1995}}
    Let \(A \in \cob\) be finite flat. Then there is a \(\cob\)-morphism \(f\colon \tilde A \to A\) 
    where \(\tilde A\) is a finite flat complete intersection and \(f\) induces an isomorphism on the tangent spaces,
    \(\tilde f \colon \phi_{\tilde{A}} \xrightarrow{\sim} \phi_A\).
\end{lemma}
\begin{proof}
    First, we notice that \(\ker \pi_A\) is a finitely generated \(O\)-module.
    This follows from the fact that submodules of finitely generated modules over PIDs
    are finitely generated again.
    Let \(a_1, \dots, a_n\) be generators of \(\ker \pi_A\). Then define
    \[
        f\colon V \coloneqq \mathcal{O}[X_1, \dots, X_n] \to A  
    \]
    via \(f(X_i) = a_i\).
    Analogous to the proof of \cref{rem:quotientofU}, we see that \(f\) is surjective.
    As usual, we define \(\pi_V\) via \(X_i \mapsto 0\;\; \forall i\).
    It is clear that
    \[
        \phi_V \coloneqq \ker \pi_V/(\ker \pi_V)^2 = \mathcal{O}X_1 \oplus \dots \oplus \mathcal{O}X_n
    \] 
    is a finitely generated \(\mathcal{O}\)-module of rank \(n\).
    Therefore the kernel of the projection \(\phi_V \to \phi_A\) is also finitely generated 
    of rank \(n' \leq n\).
    Independent of \(n'\), we can choose \(n\) possibly linearly dependent linear polynomials 
    \(\overline{f_i} \in \ker(\phi_V \to \phi_A)\) without constant term that generate 
    \(\ker \phi_V \to \phi_A\).
    Now consider a system \((f_1, \dots, f_n)\) of lifts to \(\ker f\) and denote their maximal degree with \(m\).
    All elements of \(\ker \pi_A\) can be written as a linear combination of the generators \(a_i\), so a fortiori
    we find linear polynomials \(h_i(X_1, \dots, X_n)\) s.t. \(a_i^2 = h_i(a_1, \dots, a_n)\).
    With these additional relations we can replace the relations \(f_i\) by modified relations
    \[
        f_i + X_i^mh_i - X_i^{m+2}.  
    \]
    Now we see that \(V/(f_1, \dots, f_n)\) is a finitely generated \(\mathcal{O}\)-module, 
    because it is generated by the images of monomials of degree \(\leq n(m+1)\). Indeed, any monomial
    of higher degree must contain one of the \(X_i\) at least to the power of \(m+2\). Then, using
    the relation \(f_i + X_i^mh_i - X_i^{m+2}\), it can be expressed as a sum of 
    monomials of lower degree.
    Therefore we get a surjection 
    \[
        \mathcal{O}[X_1, \dots, X_n]/(f_1, \dots, f_n) \to A.  
    \]
    The completion of the left side is still a finitely generated \(\mathcal{O}\)-module.
    %Take any power series
    %\[
    %    F = \sum_{j=0}^\infty \sum_{j_1 + \dots + j_n = j} a_{j_1, \dots, j_n} X_1^j_1 \cdot \dots \cdot X_n^j_n 
    %    \in \mathcal{O}[[X_1, \dots, X_n]]/(f_1, \dots, f_n) \eqqcolon \tilde A.
    %\]
    %Then, every \(X_1^j_1 \cdot \dots \cdot X_n^j_n\) can be written as a sum of monomials with maximal degree
    %\(n \cdot (m+1)\). Using this relations, we get
    %\[
    %    F = \sum_{j=0}^{n(m+1)} \sum_{j_1 + \dots + j_n = j} \alpha(j_1, \dots, j_n) X_1^j_1 \cdot \dots \cdot X_n^j_n,
    %\]
    %where \(\alpha(j_1, \dots, j_n)\) is a series of \(a_{\tilde j_1, \dots, \tilde j_n}\) 
    %with coefficients in \(\mathcal{O}\). This is welldefined because \(\mathcal{O}\) is complete.
    Indeed, the submodule \(M\) generated by the generators of \(\mathcal{O}[X_1, \dots, X_n]/(f_1, \dots, f_n)\) 
    contains the dense subset of all polynomials in \(\mathcal{O}[[X_1, \dots, X_n]]/(f_1, \dots, f_n)\).
    Once we can show that the \(\mathcal{O}\)-submodules generated by a single polynomial are closed in 
    \(\mathcal{O}[[X_1, \dots, X_n]]/(f_1, \dots, f_n)\), it follows that \(M\) is closed
    as a finite union of closed submodules. Consider the submodule \(f \cdot \mathcal{O}\).
    For any family of elements \((F_i)_{i \in I}\) of \(f \cdot \mathcal{O}\), we have a family 
    \((x_i)_{i \in I}\) with \(x_i \in \mathcal{O} \; \forall i \in I\) s.t. \(F_i = f\cdot x_i \; \forall i \in I\).
    Then
    \[
        \lim\limits_{i\in I} f\cdot x_i = f \cdot \lim\limits_{i \in I} x_i = f \cdot x \in f \cdot \mathcal{O},
    \]
    because \(x \in \mathcal{O}\) as \(\mathcal{O}\) is complete. Hence, \(f\cdot \mathcal{O}\) is closed.
    We obtain that the finite generating set of \(A\) generates a dense and closed subset in \(\tilde{A}\),
    i.e. it generates \(\tilde{A}\).
    Hence, \(\tilde{A}\) is a finitely generated \(\mathcal{O}\)-module \(\in \cob\). 
    From \cref{cor:flatness} we then conclude that its flat as well and therefore
    is a complete intersection where the tangent space is the completion of 
    \[
        \phi_A = \phi_{V/(f_1, \dots, f_n)} = \phi_V/(\overline{f_1}, \dots, \overline{f_n}).
    \]
    \(\overline{f_1}, \dots, \overline{f_n}\) generate \(\ker \phi_V \to \phi_A\). Hence, analogous to the
    above argumentation, they also generate the completion \(\ker \phi_U \to \phi_A\). 
    Therefore, using \cref{rem:tangentspace}, we have an isomorphism of the tangent spaces 
    \[
        \phi_{\tilde{A}} = \phi_U/(\overline{f_1}, \dots, \overline{f_n}) \to \phi_A,
    \]
    as desired.
\end{proof}

\subsection{A criterion for complete intersections}

\begin{proposition}\textup{\cite[theorem 5.27]{Darmon1995}}\label{prop:criterionCI}
    Let \(A \in \cob\) be finite flat. If \(\# \phi_A \leq \#(\mathcal{O}/\eta_A) < \infty\), 
    then \(A\) is a complete intersection.
\end{proposition}
\begin{proof}
    Take the morphism \(f\colon \tilde{A} \to A\) from \cref{lem:resolution}.
    As \(f\) induces an isomorphism on the tangent spaces, i.e. \(\phi_{\tilde{A}} = \phi_A\), 
    we can apply \cref{lem:surjectivity_phi} and conclude that \(f\) is surjective.
    By \cref{lem:standard_ineq} we also know that \(\#\phi_{\tilde{A}} \geq \#(\mathcal{O}/\eta_{\tilde{A}})\).
    Starting with the assumption and then using both of the previous facts, we obtain
    \[
        \#(\mathcal{O}/\eta_A) \geq \#\phi_A = \#\phi_{\tilde{A}} \geq \#(\mathcal{O}/\eta_{\tilde{A}}).
    \]
    As \(\tilde{A} \twoheadrightarrow A\) is surjective, we apply \cref{lem:surjectivity_eta} 
    and deduce 
    \[
        \eta_{\tilde{A}} \subset \eta_A, \;\; \#(\mathcal{O}/\eta_{\tilde{A}}) \geq \#(\mathcal{O}/\eta_A).
    \]
    All in all, we have \(\#(\mathcal{O}/\eta_A) = \#(\mathcal{O}/\eta_{\tilde{A}})\) and because of
    \(\eta_{\tilde{A}} \subset \eta_A\) we conclude \(\eta_{\tilde{A}} = \eta_A\).
    By \cref{prop:eta_iso} it follows that \(f\) is an isomorphism.
    Since \(\tilde{A}\) is a complete intersection, so is \(A\).
\end{proof}

\subsection{Proof of Wiles' numerical criterion}

\begin{proposition}\textup{\cite[theorem 5.28]{Darmon1995}}\label{prop:aimpliesc}
    Let \(R, T \in \cob\) such that \(T\) is finite flat and 
    \(\phi\colon R \twoheadrightarrow T\) is a surjective \(\cob\)-morphism.
    If \(\# \phi_R \leq \#(\mathcal{O}/\eta_T) < \infty\), then \(R\) and \(T\) are complete intersections,
    and \(\phi\) is an isomorphism.
    A fortiori, (a) \(\implies\) (c) in \cref{thm:wiles_numerical_criterion}.
\end{proposition}
\begin{proof}
    Concatenating the inequalities from \cref{lem:standard_ineq}, 
    \cref{cor:surjectivity_phi} (which is applicable because of the surjectivity of \(\phi\))
    and from the assumption, we obtain
    \[
        \#(\mathcal{O}/\eta_T) \leq \#\phi_T \leq \#\phi_R \leq \#(\mathcal{O}/\eta_T).
    \]
    All inequalities must be equalities and from \(\#\phi_T = \#(\mathcal{O}/\eta_T)\)
    we conclude with \cref{prop:criterionCI} that \(T\) is a complete intersection.
    From \(\#\phi_T = \#\phi_R \) we see that \(\phi\) induces an isomorphism on the tangent spaces.
    From \cref{prop:phi_iso} it follows that \(\phi\colon R \to T\) is an isomorphism and, 
    a fortiori \(R\) is a complete intersection as well.
\end{proof}

Now we can put all results together and complete the proof of \cref{thm:wiles_numerical_criterion}.
\begin{proof}
    The equivalence of (a) and (b) has been established in \cref{prop:aequalsb}.
    \Cref{cor:cimpliesb} shows that (c) \(\implies\) (b) in \cref{thm:wiles_numerical_criterion}.
    Finally, \cref{prop:aimpliesc} gives us the implication (a) \(\implies\) (c).
\end{proof}

\newpage
\printbibliography

\end{document}