For a given contact manifold, one can define a partial order by the following relation
\[
    \alpha \geq \beta \Leftrightarrow \exists \text{ smooth function } f: M \to \mathbb R_{\geq 1} \text{ s.t. } \alpha = f \cdot \beta.
\]
\begin{definition}[k-ADC]cf.~\cite[Definition 2.5]{BGMZ22}
    A contact structure $(M, \xi)$ is called asymptotically dynamically convex, if there is an ordered sequence of contact forms 
    $\alpha_1 \geq \alpha_2 \geq \dots \geq \alpha_i \geq \dots$ and a sequence of real numbers $D_i \to \infty$
    with the following property:
    All contractible periodic orbits of the Reeb vector field $R_{\alpha_i}$ with $\alpha_i$-action $\leq D_i$ are non-degenerate
    and have degree $> k$.
\end{definition}

Let $n \geq 4$ (for $n = 3$, a similar but more complicated argument gives the same result).
According to \cite{vK08}, the Brieskorn sphere $\Sigma_{n-1}$ is index-positive, i.e. for a given contact form $\alpha$, all contractible periodic orbits
are non-degenerate and have positive degree.
In particular, by choosing $\alpha_i = \alpha$ and $D_i$ to be any ascending sequence, $\Sigma_{n-1}$ is 0-ADC.
Then, by the following lemma, the Bourgeois manifold $S^{2n-1} \times T^2$ is 1-ADC (in this case it actually shows that it's 2-ADC but one only needs 1-ADC).

\begin{lemma} cf.~\cite[Lemma 2.8]{BGMZ22}\label{binding_adc}
    If the binding of an open book decomposition is $k$-ADC, then the corresponding Bourgeois manifold is $(k+2)$-ADC.
\end{lemma}
The proof uses the specific Reeb dynamics as computed in section \cref{reeb_dynamics}, but it is omitted here.

According to \cite[Proposition 3.2 5 (c)]{BGMZ22}, 1-ADC contact manifolds are algebraically tight.
A manifold is algebraically tight if the contact homology doesn't vanish, i.e. this is the step where the holomorphic curves are hidden.

As algebraic tightness is preserved under contact surgery, the contact structure on $S^{2n+1}$ is algebraically tight, too.
Finally, algebraic tightness implies tightness.