\section*{Surgery}
Our goal is to construct a contact structure on $S^{2n+1}$. 
Currently, we have a contact structure on $S^{2n-1} \times T^2$.
Therefore, we perform multiple contact surgeries.
First, we construct the necessary smooth surgeries. 
Then we will show that by some $h$-principle they can be realized as contact surgeries.

\paragraph*{Smooth}
According to the paper by John Milnor, we can kill $p$-homotopy classes
if $2n + 1 \geq 2p + 2$  (i.e. $n > p$) and there exists an embedding $f: S^p \times D^{2n+1-p} \to W$ 
representing the homotopy class we wish to kill, where $W$ is the manifold under consideration.
When does such an embedding exist?
Let $TW$ be the tangent bundle of $W$ and $f_0\colon S^p \to W$ a representative of the homotopy class $\lambda$. Consider the induced bundle $f_0^*(TW)$ over $S^p$.
\begin{lemma} %cite milnor, lemma 3 here
    Assume that $n \coloneqq \dim W \geq 2p+1$. Then there exists an imbedding
    \[
        S^p \times D^{n-p} \to W
    \]
    which represents $\lambda$ if and only if the induced bundle $f_0^*(TW)$ is trivial.
\end{lemma}

If the induced bundle were nontrivial, we would have an embedding of a Mobius strip into the manifold (\underline{really?}).
Therefore, it has to be trivial. After killing the first generator of $H_1$,
the manifold is still orientable, so that we can perform another $1$-surgery
to kill the second generator of $H_1$.

$1$-surgery doesn't affect $H_2$ (by general position?), so therefore we
have $\pi_2 = H_2 = \mathbb Z$ (by the Hurewicz theorem?).

%use the künneth formula


\begin{lemma}
    A simply connected homology sphere is homeomorphic to the sphere.
\end{lemma}
\begin{proof}
    Let $M^n$ be a simply connected CW-complex that is a homology sphere, i.e. $H^0(M) = \mathbb Z$ and $H^n(M) = \mathbb Z$. 
    As $M$ is simply connected, i.e. $\pi_1(M) = 0$, we can apply the Hurewicz theorem, which in turn tells us that
    \[
    \pi_k(M) = 0 \; \forall 1 < k < n\text{ and }\pi_n(M) = H^n(M) = \mathbb Z.
    \]
    As a result, $M$ is a homotopy sphere.
    Consider a generator $f: S^n \to M$ of $\pi_n(M)$.
    On $\pi_0$ level, we map one connected component to one connected component, so here the induced map is obviously bijective.
    On $\pi_k$ level with $0 < k < n$, we just map $0$ to $0$ which is an isomorphism.
    On $\pi_n$ level, we need to show that 
    \[
        f_*: \mathbb Z = \pi_n(S^n) \to \pi_n(M) = \mathbb Z 
    \]
    is an isomorphism. The identity map is a generator for $\pi_n(S^n)$. Now $f_*(\mathrm{id}) = f$, so we obtain a generator of $\pi_n(M)$. A map from $\mathbb Z \to \mathbb Z$ that sends $1$ to $1$ is a group isomorphism. These considerations show that $f$ is a weak homotopy equivalence.
    As a smooth manifold, $M$ is a CW-complex. By Whiteheads theorem we conclude that $f$ is a homotopy equivalence, so together with the generalized Poincar\'e conjecture, we have shown that $M$ is homeomorphic to the sphere.
\end{proof}

\begin{lemma}
    A simply connected homology sphere that bounds a homology ball is diffeomorphic to the sphere.
\end{lemma}
\begin{proof}
    According to the last lemma, the homology sphere $M$ is homotopy equivalent to a sphere.

    As $W$ is a zimply connected homology ball, all homotopy groups $\pi_{\ge 1}$ are 0 by the Hurewicz theorem.
    Taking any constant map on $W$ therefore is a homotopy equivalence by Whiteheads theorem, i.e. $W$ is contractible. 
    Then, cut out a ball inside $W$, s.t. we obtain a cobordism $W'$ from a sphere to $M$.
    Prove that $W'$ is an $h$-cobordism.
    Thus, by the $h$-cobordism theorem (Ranicki, Theorem 1.9), we conclude that
    $M$ is diffeomorphic to a sphere.
\end{proof}